---
title: "Factor analysis within-person"
author: "Anne Margit"
date: "6/15/2020"
output: github_document
---

This is the confirmatory factor analysis of within-person emotion scores, using person-mean centered scores

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packagages, include=FALSE, warning=FALSE}
library(psych)
library(dplyr)
library(tidyverse)
library(lavaan)  
library(ggplot2)
library(corrplot)
library(knitr)
```

```{r, results = "hide"}
load("data_long_min3.Rdata")
load("data_means.Rdata")
```

```{r, results = "hide"}
data_long_min3 <- as_tibble(data_long_min3)
data_factor <- data_long_min3 %>% select(X, Wave, Ang, Anxiety, Bored, Calm, Content, Depr, Energ, Exc, Exh, Insp, Lov, Nerv, Rel)
```


```{r}
data_factor_pmeans <- data_factor %>%
  group_by(X) %>%
  mutate_at(
    c("Ang", "Anxiety", "Bored", "Calm", "Content", "Depr", "Energ", "Exc", "Exh", "Insp", "Lov", "Nerv", "Rel"),
    funs(mean), na.rm=TRUE)
```

```{r, results = "hide"}
data_factor_new <- left_join(data_factor, data_means, by="X")
```

This dataframe data_within contains the raw scores - person means
Excited and Content are only measured on baseline, so better to delete those

```{r, results = "hide"}
data_within <- data_factor_new %>%
group_by(X) %>%
  transmute(Wave = Wave,
    Ang = Ang.x - Ang.y,
         Bored = Bored.x - Bored.y,
         Anxiety = Anxiety.x - Anxiety.y,
         Calm = Calm.x - Calm.y,
         Content = Content.x - Content.y,
         Depr = Depr.x - Depr.y,
         Energ = Energ.x - Energ.y,
         Exc = Exc.x - Exc.y,
         Exh = Exh.x - Exh.y,
         Insp = Insp.x - Insp.y,
         Lov = Lov.x - Lov.y,
         Nerv = Nerv.x - Nerv.y,
         Rel = Rel.x - Rel.y)
```

Without excited and content
```{r, results = "hide"}
data_within2 <- data_factor_new %>%
group_by(X) %>%
  transmute(Wave = Wave,
    Ang = Ang.x - Ang.y,
         Bored = Bored.x - Bored.y,
         Anxiety = Anxiety.x - Anxiety.y,
         Calm = Calm.x - Calm.y,
         Depr = Depr.x - Depr.y,
         Energ = Energ.x - Energ.y,
         Exh = Exh.x - Exh.y,
         Insp = Insp.x - Insp.y,
         Lov = Lov.x - Lov.y,
         Nerv = Nerv.x - Nerv.y,
         Rel = Rel.x - Rel.y)
```


```{r, results = "hide"}
save(data_within2, file = "data_within2.Rdata")
```

```{r}
round(cor(data_within2[,c("Ang", "Anxiety", "Bored", "Depr","Exh","Nerv","Calm","Energ", "Insp", "Lov","Rel")],use= "pairwise.complete.obs"),2)
```

```{r}
corrplot(cor(data_within2[,c("Ang", "Anxiety", "Bored", "Depr","Exh","Nerv","Calm","Energ", "Insp", "Lov","Rel")], use="pairwise.complete.obs"), order = "original", tl.col='black', tl.cex=.75)
```

```{r, results = "hide"}
model <- '
f1 =~ Ang + Anxiety + Bored + Depr + Exh + Nerv 
f2 =~ Calm + Energ + Insp + Lov + Rel 

# latent variable variances
f1 ~~ 1*f1
f2 ~~ 1*f2

# latent variable covariances
f1 ~~ f2

# manifest variable variances (uniquenesses)
  Ang ~~ Ang
  Anxiety ~~ Anxiety
  Bored ~~ Bored
  Depr ~~ Depr
  Exh ~~ Exh
  Nerv ~~ Nerv
  Calm ~~ Calm
  Energ ~~ Energ
  Insp ~~ Insp
  Lov ~~ Lov
  Rel ~~ Rel

#manifest variable means 
  Ang ~ 1
  Anxiety ~ 1
  Bored ~ 1
  Depr ~ 1
  Exh ~ 1
  Nerv ~ 1
  Calm ~ 1
  Energ ~ 1
  Insp ~ 1
  Lov ~ 1
  Rel ~ 1
'
```

```{r, results = "hide", warning = FALSE}
fit <- cfa(model, data = data_within2, std.lv=TRUE, missing="fiml")
```

```{r}
summary(fit, standardized=TRUE, fit.measures=TRUE)
```

Factor loadings for within-person factor analysis based on person-mean centered deviation scores
```{r}
parameterEstimates(fit, standardized=TRUE) %>% 
  filter(op == "=~") %>% 
  select('Latent Factor'=lhs, Indicator=rhs, B=est, SE=se, Z=z, 'p-value'=pvalue, Beta=std.all) %>% 
  kable(digits = 3, format="pandoc", caption="Factor Loadings")
```

With Lavaan package based on raw scores
```{r, results = "hide"}
model2 <- '
level: 1
f1 =~ Ang + Anxiety + Bored + Depr + Exh + Nerv 
f2 =~ Calm + Energ + Insp + Lov + Rel 

level: 2
f1 =~ Ang + Anxiety + Bored + Depr + Exh + Nerv 
f2 =~ Calm + Energ + Insp + Lov + Rel 
'
```

```{r, results = "hide",warning=FALSE}
fit2 <- cfa(model2, data = data_long_min3, std.lv=TRUE, missing="fiml", cluster="X")
```

```{r}
summary(fit2, standardized=TRUE, fit.measures=TRUE)
```

```{r}
parameterEstimates(fit2, standardized=TRUE) %>% 
  filter(op == "=~") %>% 
  select('Latent Factor'=lhs, Indicator=rhs, B=est, SE=se, Z=z, 'p-value'=pvalue, Beta=std.all) %>% 
  kable(digits = 3, format="pandoc", caption="Factor Loadings")
```







