---
title: "PAA second analyses complete"
author: "Anne Margit"
date: "04/23/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, set-options, echo=FALSE, cache= FALSE}
options(width=1000)
Sys.getenv('R_MAX_VSIZE')
```

```{r, results = "hide"}
load("data_analyse2_p1.Rdata")
load("data_analyse2_p2.Rdata")
load("data_analyse2_p3.Rdata")
```

This dataset includes:

1. Data from all weekly measurement waves (baseline through wave 11, Time 1 through 12) 
2. Participants who provided at least 3 measurements 
3. Participants who are residents of the country they currently live in
4. Participants who provided info on age
5. Participants who provided info on gender (either male or female)
6. Data from countries with at least 20 participants
7. Pooled age groups
8. Imputed missing emotion scores
9. Combined emotion scores (NAA, NAD, PAA, PAD)
10. An imputed Stringency index (StringencyIndex_imp) 
11. A dummy Str_dummy with 0 = before the peak, 1 = during peak, 2 = after peak
12. A variable indicating the number of days before maximum stringency was reached (DaysMax_p1), during (DaysMax_p2), and after (DaysPhase3)
13.  A variable indicating the number of weeks before maximum stringency was reached (WeeksMax_p1), during (WeeksMax_p2), and after (WeeksPhase3)
14. A variable indicating the date on which maximum Stringency was reached for that country (DateMaxStr) and the max level reached (MaxStr) across the entire measurement period
15. A variable indicating the date on which minimum Stringency was reached for that country (DateMinStr) and the min level reached (MinStr) across the entire measurement period
15. Observations during which there was a second peak are excluded (N=583) 

> My comments are in block quotes such as this. 

```{r, message=F}
library(dplyr)
library(tidyverse)
library(ggpubr)
library(ggplot2)
library(rockchalk)
library(effects)
library(nlme)
library(lattice)
library(broom.mixed)
library(purrr)
library(stargazer)
library(viridis)
```

# Descriptives
**Number of participants per age group**

> 0 = 18-24, 1 = 25-44, 3= 45-64, 4= 65+

Phase 1
```{r, message=F, comment=NA}
data_analyse2_p1 %>%
  group_by(Age_new) %>%
  summarise(NAge = n())
```

Phase 2
```{r, message=F, comment=NA}
data_analyse2_p2 %>%
  group_by(Age_new) %>%
  summarise(NAge = n())
```

Phase 3
```{r, message=F, comment=NA}
data_analyse2_p2 %>%
  group_by(Age_new) %>%
  summarise(NAge = n())
```

**Plots**
**Mean PAA against max stringency in WEEKS**
Phase 1 (only age differences)
```{r, echo=T, message=F, warning=F}
plot_PAA1 <- ggplot(data_analyse2_p1, aes(x=Age_new, y=PAA, group = Age_new, color = Age_new))

plot_PAA1 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0.5) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

Phase 2
```{r, echo=T, message=F, warning=F}
plot_PAA2 <- ggplot(data_analyse2_p2, aes(x=WeeksMax_p2, y=PAA, group = Age_new, color = Age_new))

plot_PAA2 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

Phase 3
```{r, echo=T, message=F, warning=F}
plot_PAA3 <- ggplot(data_analyse2_p3, aes(x=WeeksPhase3, y=PAA, group = Age_new, color = Age_new))

plot_PAA3 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

**Mean NAD against max stringency in DAYS**
Phase 2
```{r, echo=T, message=F, warning=F}
plot_PAA2 <- ggplot(data_analyse2_p2, aes(x=DaysMax_p2, y=PAA, group = Age_new, color = Age_new))

plot_PAA2 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

Phase 3
```{r, echo=T, message=F, warning=F}
plot_PAA3 <- ggplot(data_analyse2_p3, aes(x=DaysPhase3, y=PAA, group = Age_new, color = Age_new))

plot_PAA3 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

# Phase 1
*Random: IC for ID and Country + Covariates Gender and Education*

> Gender: Male = 0, Female = 1

> Edu: 0= Primary education, 1= General secondary education, 2= Vocational education, 3= Higher education, 4= Bachelors degree, 5= Masters degree, 6= PhD degree

```{r, message=F, comment=NA}
data_analyse2_p1$Edu <- as.numeric(data_analyse2_p1$Edu)
model_PAAp1 <- lme(fixed = PAA ~ Gender + Edu + Age_new,
                  random = ~1 | Country/ID, 
                  data = data_analyse2_p1, 
                  na.action = na.omit)

summary(model_PAAp1)
VarCorr(model_PAAp1)
```

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_PAAp1)
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_PAAp1 <- effect("Age_new", model_PAAp1)

plot_PAAp1 <- ggplot(as.data.frame(ef_PAAp1), 
  aes(Age_new, fit, color=Age_new)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_minimal(base_size=10) + 
  labs(title="PAA during tightening of restrictions", y = "PAA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_discrete(name ="Age", labels=c("18-24", "25-44", "45-64", "65+")) +
  theme(legend.position = "none") +                 
  scale_color_discrete() + 
  expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_PAAp1
```

*Effect sizes*
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p1 %>% 
  group_by(ID) %>%
  summarize_at(c("PAA"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("PAA"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect size = regression coefficient / average ISD of PAA

```{r, message=F, comment=NA}
coef_PAAp1 = tidy(model_PAAp1, 
               effects = "fixed")

coef_PAAp1 <- coef_PAAp1 %>%
  mutate (e_size = estimate/0.467823) %>% 
  mutate(across(2:7, round, 2)) 
         
```

```{r}
coef_PAAp1
coef_PAAp1 <- as.matrix(coef_PAAp1)
```

# Phase 2

*Best model*

> Random intercept for ID and Country, random slope for ID, no correlation between IC and S for ID + AR correlation structure at Measurement level

```{r, message=F, comment=NA}
data_analyse2_p2$Edu <- as.numeric(data_analyse2_p2$Edu)
data_analyse2_p2 <- data_analyse2_p2[with(data_analyse2_p2, order(Country, ID, Time)),]
data_analyse2_p2$Time <- as.numeric(data_analyse2_p2$Time)

model_PAAp2 <- lme(fixed = PAA ~ Gender + Edu + DaysMax_p2 + Age_new + DaysMax_p2*Age_new,
                  random = list(Country = ~1, ID = pdDiag(~DaysMax_p2)),
                  data = data_analyse2_p2, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~Time | Country/ID))

summary(model_PAAp2)
VarCorr(model_PAAp2)
```

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_PAAp2, which = 'fixed')
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_PAAp2 <- effect("DaysMax_p2:Age_new", model_PAAp2)

plot_PAAp2 <- ggplot(as.data.frame(ef_PAAp2), aes(DaysMax_p2, fit, color=Age_new)) + 
  geom_line(size=1) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + 
  theme_minimal(base_size=10) + 
  labs(title="A",
       x="Days", y = "PAA") +
  theme(plot.title = element_text(size=10)) +
  scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + 
  expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_PAAp2
```

*Effect sizes*
**Within person SD and average within person SD**
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p2 %>% 
  group_by(ID) %>%
  summarize_at(c("DaysMax_p2", "PAA"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("DaysMax_p2", "PAA"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect sizes for intercept and main effect of age and covariates = regression coefficient / average ISD of PAA
> Effect size for main effect of DaysMax = (regression coefficient * 28)/ average ISD of PAA
> Effect sizes for interaction effects = (regression coefficient * 28)/ average ISD of PAA

> The effect sizes for main effect of DaysMax and the interaction effects reflect the increase in SD of PAA over 4 weeks (28 days)

```{r, message=F, comment=NA}
coef_PAAp2 = tidy(model_PAAp2, 
               effects = "fixed")

coef_PAAp2 <- coef_PAAp2 %>%
  mutate(e_size = ifelse(row_number()== 1 | row_number()== 2 |  row_number()== 3 |  row_number()== 5 |  row_number()== 6 |  row_number()== 7,  estimate/0.4890815, (estimate*28)/0.4890815)) %>%
  mutate(across(2:7, round, 2)) 
          
```

```{r}
coef_PAAp2
coef_PAAp2 <- as.matrix(coef_PAAp2)
```

> PAA increases over time in the youngest age group (main effect), and also increases in the older groups but more slowly (interaction effect). There are no significant differences in PAA between age groups on the first day of max stringency (main effect). Women report lower PAA compared to men, and higher educated people report higher PAA compared to lower educated people. 

```{r}
model_coefs <- coef(model_PAAp2, level = 2)
  
model_coefs <- as.data.frame(model_coefs) %>%
rownames_to_column("ID")
  
model_coefs <- model_coefs %>%
separate(col = 1, into = c("Country", "ID"), sep = "\\/") %>%
dplyr::rename("Intercept" = "(Intercept)")
  
data2 <- left_join(data_analyse2_p2, model_coefs, by= "ID")
  
data3 <- data2 %>%
filter(Nmiss == 0) %>%
  filter(n > 5)
```

```{r}
labels <- c("0" = "Age 18-24", "1" = "Age 25-44", "2" = "Age 45-64", "3" = "Age 65+")

model_coef_plot <- ggplot(data = data3[which(data3$ID2 <200),], 
       mapping = aes(x = DaysMax_p2.x, y = PAA, colour = ID)) +
       geom_point() +
       geom_abline(aes(intercept = Intercept, 
                  slope = DaysMax_p2.y,
                  colour = ID),size = 0.5) + 
                  scale_x_continuous(limits = c(0, 100)) + 
                  theme(legend.position = "none") +
                  facet_wrap(~Age_new, 
                  labeller = labeller(Age_new = labels)) +
      xlab("Days") +
      ggtitle("Predicted PAA trajectories for subsample of participants") +
      theme_minimal(base_size=10) + 
      scale_color_discrete() + 
      theme(plot.title = element_text(hjust = 0.5)) +
      theme(panel.spacing.x = unit(1, "lines")) +
      theme(legend.position = "none") 

model_coef_plot
```

# Random slope variation plot
```{r, message=F}
Age_labels <- c("Age 18-24", "Age 25-44", "Age 45-64", "Age 65+")
names(Age_labels) <- c("0","1","2","3")

plot_PAAp2_slope <- ggplot(data2, aes(x= DaysMax_p2.y, fill = ..x..)) +
  geom_histogram() +
  scale_x_continuous(breaks = seq(-0.02, 0.02, 0.01)) +
  scale_y_continuous(breaks = seq(0, 2000, 500)) +
 scale_fill_viridis(option = "C")+
  theme_minimal(base_size=10)+
  theme(legend.position="none") + 
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "grey", size=.5) + 
  labs(title="A",
       x="Regression coefficient (PAA ~ days)", y = "Count") +
  theme(plot.title = element_text(size=10)) +
  theme(panel.spacing.x = unit(1, "lines")) +
   facet_wrap(~ Age_new, labeller = labeller(Age_new = Age_labels)) 
```

```{r}
plot_PAAp2_slope 

```

Distribution 
```{r}
data2<- as_tibble(data2)
data2 %>%
  filter(DaysMax_p2.y > 0) %>%
  summarise(N = n())

#29416

data2 %>%
  filter(DaysMax_p2.y < 0) %>%
  summarise(N = n())

#170

#Decrease in PAA:

170 / (170 + 29416) * 100

#0.57%

```
Mean regression coefficients per country
```{r, message=F, comment=NA}
reg_country_PAA <- data2 %>%
  group_by(Country.x) %>%
  summarise(reg_mean = mean(DaysMax_p2.y, na.rm=TRUE), reg_sd = sd (DaysMax_p2.y, na.rm=TRUE), reg_min = min(DaysMax_p2.y, na.rm=TRUE), reg_max=max(DaysMax_p2.y, na.rm=TRUE)) %>%
  mutate(across(2:5, round, 3))

```

```{r, message=F, comment=NA}
reg_country_PAA %>% summarise(max_across = max(reg_mean), min_across = min(reg_mean))
```

# Quadratic term
The interaction between age and daysmax was significant so these are kept in the current model. The time variable needs to be centered at the midpoint (mean) to reduce collinearity between the linear and the quadratic components.

```{r, message=F, comment=NA}
data_analyse2_p2q <- gmc(data_analyse2_p2, "DaysMax_p2", "ID", FUN = mean, suffix = c("_mn", "_dev"),
    fulldataframe = TRUE)
```


```{r, message=F, comment=NA}
data_analyse2_p2q$Edu <- as.numeric(data_analyse2_p2q$Edu)

data_analyse2_p2q <- data_analyse2_p2q[with(data_analyse2_p2q, order(Country, ID, Time)),]
data_analyse2_p2q$Time <- as.numeric(data_analyse2_p2q$Time)

model_PAAp2q <- lme(fixed = PAA ~ Gender + Edu + DaysMax_p2_dev + Age_new + DaysMax_p2_dev*Age_new +  
                    + I(DaysMax_p2_dev^2) + I(DaysMax_p2_dev^2)*Age_new,
                  random = list(Country = pdDiag(~ DaysMax_p2_dev), 
                  ID = ~DaysMax_p2_dev),
                  data = data_analyse2_p2q, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_PAAp2q)
VarCorr(model_PAAp2q)

```

Results suggest that there is a linear increase of PAA over time in the youngest age group and a slower increase in the older age groups. There was no significant quadratic effect.


*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_PAAp2q, which = 'fixed')
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_PAAp2q <- effect("Age_new:I(DaysMax_p2_dev^2)", model_PAAp2q)

plot_PAAp2q <- ggplot(as.data.frame(ef_PAAp2q), aes(DaysMax_p2_dev, fit, color=Age_new)) + 
  geom_line(size=1) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + 
  theme_minimal(base_size=10) + 
  labs(title="Quadratic PAA trajectories during peak restrictions",
       x="Days  (centered)", y = "PAA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + 
  expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_PAAp2q
```

# Phase 3

> Random: IC for ID and Country, S for ID, no correlation between IC and S for ID + AR

```{r, message=F, comment=NA}
data_analyse2_p3$Edu <- as.numeric(data_analyse2_p3$Edu)
data_analyse2_p3 <- data_analyse2_p3[with(data_analyse2_p3, order(Country, ID, Time)),]
data_analyse2_p3$Time <- as.numeric(data_analyse2_p3$Time)

model_PAAp3 <- lme(fixed = PAA ~ Gender + Edu + DaysPhase3 + Age_new + DaysPhase3*Age_new,
                  random = list (Country = ~1, ID = pdDiag(~DaysPhase3)), 
                  data = data_analyse2_p3, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_PAAp3)
VarCorr(model_PAAp3)
```

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_PAAp3, which = 'fixed')
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_PAAp3 <- effect("DaysPhase3:Age_new", model_PAAp3)

plot_PAAp3 <- ggplot(as.data.frame(ef_PAAp3), aes(DaysPhase3, fit, color=Age_new)) + 
  geom_line(size=1) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + 
  theme_minimal(base_size=10) + 
  labs(title="B",
       x="Days", y = "PAA") +
  theme(plot.title = element_text(size=10)) +
  scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + 
  expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_PAAp3
```

```{r, message=F}
plot_PAAp2and3 <- ggarrange(plot_PAAp2, plot_PAAp3 , 
          ncol = 2, nrow = 1, common.legend=TRUE, legend= "bottom")

plot_PAAp2and3 <- annotate_figure(plot_PAAp2and3,top = text_grob("PAA trajectories during peak (A) and easing (B) of restrictions", size = 12))
  
  
```
```{r, message=F}
plot_PAAp2and3
  
```

*Effect sizes*
**Within person SD and average within person SD for PAA**
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p3 %>% 
  group_by(ID) %>%
  summarize_at(c("PAA"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("PAA"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect sizes for intercept and main effect of age = regression coefficient / average ISD of PAA
> Effect size for main effect of DaysMax = (regression coefficient * 28)/ average ISD of PAA
> Effect sizes for interaction effects = (regression coefficient * 28)/ average ISD of PAA

> The effect sizes for main effect of DaysMax and the interaction effects reflect the increase in SD of PAA over 4 weeks (28 days)

```{r, message=F, comment=NA}
coef_PAAp3 = tidy(model_PAAp3, 
               effects = "fixed")

coef_PAAp3 <- coef_PAAp3 %>%
 mutate(e_size = ifelse(row_number()== 1 | row_number()== 2 |  row_number()== 3 |  row_number()== 5 |  row_number()== 6 |  row_number()== 7,  estimate/0.4894064, (estimate*28)/0.4894064)) %>%
  mutate(across(2:7, round, 2)) 
```

```{r}
coef_PAAp3
coef_PAAp3 <- as.matrix(coef_PAAp3)
```

> PAA increases over time in the youngest group (main effect) and older groups with the same degree (interaction effect). There are no age differences in PAA on the first day stringency reduces again after the peak (main effect). Women report lower PAA, two higher educated groups report higher PAA. 

```{r}
model_coefs <- coef(model_PAAp3, level = 2)
  
model_coefs <- as.data.frame(model_coefs) %>%
rownames_to_column("ID")
  
model_coefs <- model_coefs %>%
separate(col = 1, into = c("Country", "ID"), sep = "\\/") %>%
dplyr::rename("Intercept" = "(Intercept)")
  
data2 <- left_join(data_analyse2_p3, model_coefs, by= "ID")
  
data3 <- data2 %>%
filter(Nmiss == 0) %>%
  filter(n > 5)
```

```{r}
labels <- c("0" = "Age 18-24", "1" = "Age 25-44", "2" = "Age 45-64", "3" = "Age 65+")

model_coef_plot <- ggplot(data = data3[which(data3$ID2 <200),], 
       mapping = aes(x = DaysPhase3.x, y = PAA, colour = ID)) +
  geom_point() +
  geom_abline(aes(intercept = Intercept, 
                  slope = DaysPhase3.y,
                  colour = ID),size = 0.5) + 
                  scale_x_continuous(limits = c(0, 100)) + 
                  theme(legend.position = "none") +
                  facet_wrap(~Age_new, 
                  labeller = labeller(Age_new = labels)) +
  xlab("Days") +
  ggtitle("Predicted PAA trajectories for subsample of participants")  +
      theme_minimal(base_size=10) + 
      scale_color_discrete() + 
      theme(plot.title = element_text(hjust = 0.5)) +
      theme(panel.spacing.x = unit(1, "lines")) +
      theme(legend.position = "none") 

model_coef_plot
```  

# Random slope variation plot
```{r, message=F}
plot_PAAp3_slope <- ggplot(data2, aes(x= DaysPhase3.y, fill = ..x..)) +
  geom_histogram() +
 scale_fill_viridis(option = "C") +
  scale_x_continuous(breaks = seq(-0.02, 0.02, 0.01)) +
  scale_y_continuous(breaks = seq(0, 2000, 500)) +
  theme_minimal(base_size=10)+
  theme(legend.position="none") + 
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "grey", size=.5) + 
  labs(title="B",
       x="Regression coefficient (PAA ~ days)", y = "Count") +
  theme(plot.title = element_text(size=10)) +
  theme(panel.spacing.x = unit(1, "lines")) +
   facet_wrap(~ Age_new, labeller = labeller(Age_new = Age_labels)) 

```

```{r}
plot_PAAp3_slope 
```

```{r, message=F}
plot_PAAp2and3_slope <- ggarrange(plot_PAAp2_slope, plot_PAAp3_slope , 
          ncol = 2, nrow = 1)

plot_PAAp2and3_slope <- annotate_figure(plot_PAAp2and3_slope,top = text_grob("Variability in PAA trajectories during peak (A) and easing (B) of restrictions", size = 12))
  
```

```{r, message=F}
plot_PAAp2and3_slope
  
```


Distribution 
```{r}
data2<- as_tibble(data2)
data2 %>%
  filter(DaysPhase3.y > 0) %>%
  summarise(N = n())

#22510

data2 %>%
  filter(DaysPhase3.y < 0) %>%
  summarise(N = n())

#2500

#Decrease in PAA

2500 / (2500 + 22510) * 100

#10.00%

```


```{r}
stargazer(coef_PAAp1, coef_PAAp2, coef_PAAp3,
type="html", df = TRUE, out="star_coefallphase_PAA.doc",  single.row=TRUE, digits = 3, align = TRUE)

stargazer(model_PAAp1, model_PAAp2, model_PAAp2q, model_PAAp3,
type="html", df = TRUE, out="starallphasesPAA.doc",  single.row=TRUE, digits = 3, align = TRUE,
intercept.top = TRUE, intercept.bottom = FALSE)

reg_country_PAA <- as.matrix(reg_country_PAA)
stargazer(reg_country_PAA, df= TRUE, type="html", out="reg_country_PAA.doc")
```