---
title: "PAD all phases winning models"
author: "Anne Margit"
date: "10/28/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, set-options, echo=FALSE, cache= FALSE}
options(width=1000)
Sys.getenv('R_MAX_VSIZE')
```

```{r, results = "hide"}
load("data_analyse2_p1.Rdata")
load("data_analyse2_p2.Rdata")
load("data_analyse2_p3.Rdata")
```

This dataset includes:

1. Data from all weekly measurement waves (baseline through wave 11, Time 1 through 12) 
2. Participants who provided at least 3 measurements 
3. Participants who are residents of the country they currently live in
4. Participants who provided info on age
5. Participants who provided info on gender (either male or female)
6. Data from countries with at least 20 participants
7. Pooled age groups
8. Imputed missing emotion scores
9. Combined emotion scores (NAA, NAD, PAA, PAD)
10. An imputed Stringency index (StringencyIndex_imp) 
11. A dummy Str_dummy with 0 = before the peak, 1 = during peak, 2 = after peak
12. A variable indicating the number of days before maximum stringency was reached (DaysMax_p1), during (DaysMax_p2), and after (DaysPhase3)
13.  A variable indicating the number of weeks before maximum stringency was reached (WeeksMax_p1), during (WeeksMax_p2), and after (WeeksPhase3)
14. A variable indicating the date on which maximum Stringency was reached for that country (DateMaxStr) and the max level reached (MaxStr) across the entire measurement period
15. A variable indicating the date on which minimum Stringency was reached for that country (DateMinStr) and the min level reached (MinStr) across the entire measurement period
15. Observations during which there was a second peak are excluded (N=583) 

> My comments are in block quotes such as this. 

```{r, message=F}
library(dplyr)
library(tidyverse)
library(ggpubr)
library(ggplot2)
library(rockchalk)
library(effects)
library(nlme)
library(lattice)
library(broom.mixed)
library(purrr)
library(stargazer)
```

# Descriptives
**Number of participants per age group**

> 0 = 18-24, 1 = 25-44, 3= 45-64, 4= 65+

Phase 1
```{r, message=F, comment=NA}
data_analyse2_p1 %>%
  group_by(Age_new) %>%
  summarise(NAge = n())
```

Phase 2
```{r, message=F, comment=NA}
data_analyse2_p2 %>%
  group_by(Age_new) %>%
  summarise(NAge = n())
```

Phase 3
```{r, message=F, comment=NA}
data_analyse2_p2 %>%
  group_by(Age_new) %>%
  summarise(NAge = n())
```

**Plots**
**Mean PAD against max stringency in WEEKS**
Phase 1 (only age differences)
```{r, echo=T, message=F, warning=F}
plot_PAD1 <- ggplot(data_analyse2_p1, aes(x=Age_new, y=PAD, group = Age_new, color = Age_new))

plot_PAD1 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0.5) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

Phase 2
```{r, echo=T, message=F, warning=F}
plot_PAD2 <- ggplot(data_analyse2_p2, aes(x=WeeksMax_p2, y=PAD, group = Age_new, color = Age_new))

plot_PAD2 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

Phase 3
```{r, echo=T, message=F, warning=F}
plot_PAD3 <- ggplot(data_analyse2_p3, aes(x=WeeksPhase3, y=PAD, group = Age_new, color = Age_new))

plot_PAD3 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

**Mean NAD against max stringency in DAYS**
Phase 2
```{r, echo=T, message=F, warning=F}
plot_PAD2 <- ggplot(data_analyse2_p2, aes(x=DaysMax_p2, y=PAD, group = Age_new, color = Age_new))

plot_PAD2 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

Phase 3
```{r, echo=T, message=F, warning=F}
plot_PAD3 <- ggplot(data_analyse2_p3, aes(x=DaysPhase3, y=PAD, group = Age_new, color = Age_new))

plot_PAD3 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

# Phase 1
*Random: IC for ID and Country + Covariates Gender and Education*

> Gender: Male = 0, Female = 1

> Edu: 0= Primary education, 1= General secondary education, 2= Vocational education, 3= Higher education, 4= Bachelors degree, 5= Masters degree, 6= PhD degree

```{r, message=F, comment=NA}
data_analyse2_p1$Edu <- as.numeric(data_analyse2_p1$Edu)
model_PADp1 <- lme(fixed = PAD ~ Gender + Edu + Age_new,
                  random = ~1 | Country/ID, 
                  data = data_analyse2_p1, 
                  na.action = na.omit)

summary(model_PADp1)
VarCorr(model_PADp1)
```

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_PADp1)
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_PADp1 <- effect("Age_new", model_PADp1)

plot_PADp1 <- ggplot(as.data.frame(ef_PADp1), 
       aes(Age_new, fit, color=Age_new)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_bw(base_size=12) + scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_PADp1
```

*Effect sizes*
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p1 %>% 
  group_by(ID) %>%
  summarize_at(c("PAD"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("PAD"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect size = regression coefficient / average ISD of PAD

```{r, message=F, comment=NA}
coef_PADp1 = tidy(model_PADp1, 
               effects = "fixed")

coef_PADp1 <- coef_PADp1 %>%
  mutate (e_size = estimate/0.467823) %>% 
  mutate(across(2:7, round, 2)) 
         
```

```{r}
coef_PADp1
coef_PADp1 <- as.matrix(coef_PADp1)
```

# Phase 2

*Best model*

> Random intercept for ID and Country, random slope for ID and country, no correlation between IC and S for ID and country + AR correlation structure at Measurement level

```{r, message=F, comment=NA}
data_analyse2_p2$Edu <- as.numeric(data_analyse2_p2$Edu)
data_analyse2_p2 <- data_analyse2_p2[with(data_analyse2_p2, order(Country, ID, Time)),]
data_analyse2_p2$Time <- as.numeric(data_analyse2_p2$Time)

model_PADp2 <- lme(fixed = PAD ~ Gender + Edu + DaysMax_p2 + Age_new + DaysMax_p2*Age_new,
                  random = list(Country= pdDiag(~DaysMax_p2), ID = pdDiag(~DaysMax_p2)), 
                  data = data_analyse2_p2, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_PADp2)
VarCorr(model_PADp2)
```

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_PADp2, which = 'fixed')
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_PADp2 <- effect("DaysMax_p2:Age_new", model_PADp2)

plot_PADp2 <- ggplot(as.data.frame(ef_PADp2), 
       aes(DaysMax_p2, fit, color=Age_new)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_bw(base_size=12) + scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_PADp2
```

*Effect sizes*
**Within person SD and average within person SD**
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p2 %>% 
  group_by(ID) %>%
  summarize_at(c("DaysMax_p2", "PAD"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("DaysMax_p2", "PAD"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect sizes for intercept and main effect of age and covariates = regression coefficient / average ISD of PAD
> Effect size for main effect of DaysMax = (regression coefficient * 28)/ average ISD of PAD
> Effect sizes for interaction effects = (regression coefficient * 28)/ average ISD of PAD

> The effect sizes for main effect of DaysMax and the interaction effects reflect the increase in SD of PAD over 4 weeks (28 days)

```{r, message=F, comment=NA}
coef_PADp2 = tidy(model_PADp2, 
               effects = "fixed")

coef_PADp2 <- coef_PADp2 %>%
  mutate(e_size = ifelse(row_number()== 1 | row_number()== 2 |  row_number()== 3 |  row_number()== 4 |  row_number()== 5
                          |  row_number()== 6 |  row_number()== 7 |  row_number()== 8  |  row_number()== 10  
                          |  row_number()== 11  |  row_number()== 12, 
                          estimate/0.5049948, (estimate*28)/0.5049948)) %>%
  mutate(across(2:7, round, 2)) 
          
```

```{r}
coef_PADp2
coef_PADp2 <- as.matrix(coef_PADp2)
```

> PAD increases over time in the youngest age group (main effect), and also increases in the older groups but faster (interaction effect). Compared to the youngest age group, older groups report lower PAD on the first day of max stringency, except for the oldest age group (main effect). Women report lower PAD compared to men, and higher educated people report higher PAD compared to lower educated people. 

# Phase 3

> Random: IC for ID and Country, S for ID and country, no correlation between IC and S for ID and country + AR

```{r, message=F, comment=NA}
data_analyse2_p3$Edu <- as.numeric(data_analyse2_p3$Edu)
data_analyse2_p3 <- data_analyse2_p3[with(data_analyse2_p3, order(Country, ID, Time)),]
data_analyse2_p3$Time <- as.numeric(data_analyse2_p3$Time)

model_PADp3 <- lme(fixed = PAD ~ Gender + Edu + DaysPhase3 + Age_new + DaysPhase3*Age_new,
                  random = list(Country = pdDiag(~DaysPhase3), ID = pdDiag(~DaysPhase3)),
                  data = data_analyse2_p3, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_PADp3)
VarCorr(model_PADp3)
```

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_PADp3, which = 'fixed')
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_PADp3 <- effect("DaysPhase3:Age_new", model_PADp3)

plot_PADp3 <- ggplot(as.data.frame(ef_PADp3), 
       aes(DaysPhase3, fit, color=Age_new)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_bw(base_size=12) + scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_PADp3
```

*Effect sizes*
**Within person SD and average within person SD for PAD**
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p3 %>% 
  group_by(ID) %>%
  summarize_at(c("PAD"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("PAD"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect sizes for intercept and main effect of age = regression coefficient / average ISD of PAD
> Effect size for main effect of DaysMax = (regression coefficient * 28)/ average ISD of PAD
> Effect sizes for interaction effects = (regression coefficient * 28)/ average ISD of PAD

> The effect sizes for main effect of DaysMax and the interaction effects reflect the increase in SD of PAD over 4 weeks (28 days)

```{r, message=F, comment=NA}
coef_PADp3 = tidy(model_PADp3, 
               effects = "fixed")

coef_PADp3 <- coef_PADp3 %>%
 mutate(e_size = ifelse(row_number()== 1 | row_number()== 2 |  row_number()== 3 |  row_number()== 4 |  row_number()== 5
                          |  row_number()== 6 |  row_number()== 7 |  row_number()== 8  |  row_number()== 10  
                          |  row_number()== 11  |  row_number()== 12, 
                          estimate/0.493802, (estimate*28)/0.493802)) %>%
  mutate(across(2:7, round, 2)) 
```

```{r}
coef_PADp3
coef_PADp3 <- as.matrix(coef_PADp3)
```

> PAD seems to decrease over time in the youngest group but not significant (main effect), whereas it increases over time in the older age groups (interaction effect) very slightly. There are no age differences in PAD on the first day stringency reduces again after the peak, except for the oldest age group which reports higher PAD (main effect). Women report lower PAD, higher educated groups report higher PAD. 

```{r}
stargazer(coef_PADp1, coef_PADp2, coef_PADp3,
type="html", df = TRUE, out="star_coefallphase_PAD.doc",  single.row=TRUE, digits = 2, align = TRUE)

stargazer(model_PADp1, model_PADp2, model_PADp3,
type="html", df = TRUE, out="starallphasesPAD.doc",  single.row=TRUE, digits = 2, align = TRUE,
intercept.top = TRUE, intercept.bottom = FALSE)
```