---
title: "Second analysis PAA Phase 1"
author: "Anne Margit"
date: "10/14/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, set-options, echo=FALSE, cache= FALSE}
options(width=1000)
Sys.getenv('R_MAX_VSIZE')
```

```{r, results = "hide"}
load("data_analyse2_p1.Rdata")
```

This dataset includes:

1. Data from all weekly measurement waves (baseline through wave 11, Time 1 through 12) 
2. Participants who provided at least 3 measurements 
3. Participants who are residents of the country they currently live in
4. Participants who provided info on age
5. Participants who provided info on gender (either male or female)
6. Data from countries with at least 20 participants
7. Pooled age groups
8. Imputed missing emotion scores
9. Combined emotion scores (NAA, NAD, PAA, PAD)
10. An imputed Stringency index (StringencyIndex_imp) 
11. A variable indicating the number of days before and after the day on which maximum stringency was reached for the respective country (DaysMax)
12. A variable indicating the number of weeks before and after the day on which maximum stringency was reached for the respective country (WeeksMax)
13. A variable indicating the date on which maximum Stringency was reached for that country (DateMaxStr)
14. A dummy Str_dummy with 0 = before the peaj, 1 = during peak, 2 = after peak
15. Observations during which there was a second peak are excluded (N=583) 

> My comments are in block quotes such as this. 

```{r, message=F}
library(dplyr)
library(tidyverse)
library(ggpubr)
library(ggplot2)
library(rockchalk)
library(effects)
library(nlme)
library(lattice)
library(broom.mixed)
library(purrr)
```

# Descriptives
**Number of participants per age group**
```{r, message=F, comment=NA}
data_analyse2_p1 %>%
  group_by(Age_new) %>%
  summarise(NAge = n())
```

**Plots**
**Mean PAA against max stringency in WEEKS**
```{r, echo=T, message=F, warning=F}
plot_PAA <- ggplot(data_analyse2_p1, aes(x=WeeksMax_p1, y=PAA, group = Age_new, color = Age_new))

plot_PAA + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

**Mean PAA against max stringency in DAYS**
```{r, echo=T, message=F, warning=F}
plot_PAA <- ggplot(data_analyse2_p1, aes(x=DaysMax_p1, y=PAA, group = Age_new, color = Age_new))

plot_PAA + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

# Regression models phase 1

**Positive affect high arousal**

*Predictors: DaysMax_p1, Age, Random: IC for Country*
```{r, message=F, comment=NA}
model_PAA1 <- lme(fixed = PAA ~ DaysMax_p1 + Age_new + DaysMax_p1*Age_new,
                   random = ~1 | Country, 
                  data = data_analyse2_p1, 
                  na.action = na.omit)

summary(model_PAA1)
```

*Predictors: DaysMax_p1, Age, Random: IC for ID*
```{r, message=F, comment=NA}
model_PAA2 <- lme(fixed = PAA ~ DaysMax_p1 + Age_new + DaysMax_p1*Age_new,
                  random = ~1 | ID, 
                 data = data_analyse2_p1, 
                 na.action = na.omit)

summary(model_PAA2)
```

*Random: IC for ID and Country*
```{r, message=F, comment=NA}
model_PAA3 <- lme(fixed = PAA ~ DaysMax_p1 + Age_new + DaysMax_p1*Age_new,
                  random = ~1 | Country/ID, 
                  data = data_analyse2_p1, 
                  na.action = na.omit)

summary(model_PAA3)
```

*Random: IC for ID and Country, S for Country*
```{r, message=F, comment=NA}
model_PAA4 <- lme(fixed = PAA ~ DaysMax_p1 + Age_new + DaysMax_p1*Age_new,
                  random = list (Country = ~DaysMax_p1, ID = ~1), 
                  data = data_analyse2_p1, 
                  na.action = na.omit)

summary(model_PAA4)
```

*Random: IC for ID and Country, S for ID*
```{r, message=F, comment=NA}
model_PAA5 <- lme(fixed = PAA ~ DaysMax_p1 + Age_new + DaysMax_p1*Age_new,
                  random = list (Country = ~1, ID = ~DaysMax_p1), 
                  data = data_analyse2_p1, 
                  na.action = na.omit)

summary(model_PAA5)
```

*Random slope for Country and ID*
```{r, message=F, comment=NA}
model_PAA6 <- lme(fixed = PAA ~ DaysMax_p1 + Age_new + DaysMax_p1*Age_new,
                  random = ~DaysMax_p1 | Country/ID, 
                  data = data_analyse2_p1, 
                  na.action = na.omit)

summary(model_PAA6)
```

> Model without random slopes for Country and ID is best (?) PAA3 

*Random: IC for ID and Country + AR*
```{r, message=F, comment=NA}
data_analyse2_p1 <- data_analyse2_p1[with(data_analyse2_p1, order(Country, ID, Time)),]
data_analyse2_p1$Time <- as.numeric(data_analyse2_p1$Time)

model_PAA7 <- lme(fixed = PAA ~ DaysMax_p1 + Age_new + DaysMax_p1*Age_new,
                  random = ~1 | Country/ID, 
                  data = data_analyse2_p1, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_PAA7)
```

> Model met AR lijkt iets minder goed maar verschilt maar 2 BIC punten. Omdat de andere modellen wel allemaal een AR structuur hebben lijkt PAA7 me wel de beste keuze 

*QQ plot of residuals*
```{r, message=F, comment=NA}
par(mfrow = c(1,2))
lims <- c(-3.5,3.5)
hist(resid(model_PAA7, type = "normalized"),
freq = FALSE, xlim = lims, ylim =  c(0,.7),main = "Histogram of Standardized Residuals")
lines(density(scale(resid(model_PAA7))))
qqnorm(resid(model_PAA7, type = "normalized"),
xlim = lims, ylim = lims,main = "QQ plot")
abline(0,1, col = "red", lty = 2)
```

*Residuals vs fitted*
```{r, message=F, comment=NA}
plot(fitted(model_PAA7, level=2), residuals(model_PAA7, level=2), 
     main="residuals vs fitted at ID level")
abline(a=0, b=0,col="red")
plot(fitted(model_PAA7, level=1), residuals(model_PAA7, level=1), 
    main="residuals vs fitted at Country level")
abline(a=0, b=0,col="red")
```

> Residuen zien er allemaal goed uit

*Plot random intercepts and slopes*
```{r, message=F, comment=NA}
plot(ranef(model_PAA7, level = 1))
plot(ranef(model_PAA7, level = 2))
```

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_PAA7)
```
*Plot of predicted values*
```{r, results = "hide", message=F}
ef_PAA <- effect("DaysMax_p1:Age_new", model_PAA7)

plot_PAA <- ggplot(as.data.frame(ef_PAA), 
       aes(DaysMax_p1, fit, color=Age_new)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_bw(base_size=12) + scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_PAA
```

```{r, message=F, comment=NA}
coef_PAA = tidy(model_PAA7, 
               effects = "fixed")
```

*Effect sizes*
**Within person SD and average within person SD of NAA**
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p1 %>% 
  group_by(ID) %>%
  summarize_at(c("PAA"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("PAA"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```
> Effect sizes for intercept and main effect of age = regression coefficient / average ISD of PAA
> Effect size for main effect of DaysMax = (regression coefficient * 28)/ average ISD of PAA
> Effect sizes for interaction effects = (regression coefficient * 28)/ average ISD of PAA

> The effect sizes for main effect of DaysMax and the interaction effects reflect the increase in SD of PAA over 4 weeks (28 days)

```{r, message=F, comment=NA}
coef_PAA <- coef_PAA %>%
  mutate(e_size = ifelse(row_number()== 1 | row_number()== 3 |  row_number()== 4 |  row_number()== 5,
          estimate/0.4706784, 
          (estimate*28)/0.4706784))
         
```

```{r}
coef_PAA
```

> There are differences between the youngest age category with the oldest two age categories in intensity, but no change over time


