---
title: "Data prep"
date: "5/24/2020"
author:  "A.M. Reitsema"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include= FALSE}
library(dplyr)
library(anytime)
library(tidyr)
library(plyr)
library(arsenal)
library(tidyverse)
library(knitr)
library(papaja)
```

```{r load dataset corona}
coronadata <- read.csv("Data/RMD06_Anne Margit Reitsema_2020-05-08 11-48 CEST.csv", header=TRUE)
oxforddata <- read.csv("Data/OxCGRT_latest.csv", header=TRUE)
```

To check whether country names are different in both datasets:
```{r, echo= T, results='hide'}
levels1 <- levels(coronadata$coded_country)
levels2 <- levels(oxforddata$CountryName)

levels1<- as.data.frame(levels1)
levels2<- as.data.frame(levels2)

levels1$levels1 <-as.character(levels1$levels1)
levels2$levels2 <-as.character(levels2$levels2)

check <- comparedf(levels1, levels2, by.x="levels1", by.y="levels2")
summary(check)
```

Country names that need to be renamed in PsyCorona:  
Hong Kong S.A.R. -> Hong Kong  
Kyrgyzstan -> Kyrgyz Republic  
United Republic of Tanzania -> Tanzania  
United States of America -> United States  
Republic of Serbia -> Serbia  

```{r rename countries, echo= T, results='hide'}
coronadata$coded_country <- 
  revalue(coronadata$coded_country , c("Hong Kong S.A.R."="Hong Kong", 
                                       "Kyrgyzstan" = "Kyrgyz Republic",
                                       "United Republic of Tanzania" = "Tanzania", 
                                       "United States of America" = "United States",
                                       "Republic of Serbia" = "Serbia"))
```

Renaming and recoding variables:
```{r, echo= T, results='hide'}
coronadata$gender <- as.factor(coronadata$gender)
coronadata$age <- as.factor(coronadata$age)
coronadata$gender <- as.factor(coronadata$gender)
coronadata$dateB<-anydate(coronadata$StartDate)
coronadata$dateW1 <- anydate(coronadata$w1_StartDate)

names(coronadata)[names(coronadata) == "coded_country"] <- "country"
names(coronadata)[names(coronadata) == "X"] <- "ID"
```

Recoding NA into zero's:
```{r, echo= T, results='hide'}
coronadata$coronaClose_1[is.na(coronadata$coronaClose_1)] <- 0
coronadata$coronaClose_2[is.na(coronadata$coronaClose_2)] <- 0
coronadata$coronaClose_3[is.na(coronadata$coronaClose_3)] <- 0
coronadata$coronaClose_4[is.na(coronadata$coronaClose_4)] <- 0
coronadata$coronaClose_5[is.na(coronadata$coronaClose_5)] <- 0
coronadata$coronaClose_6[is.na(coronadata$coronaClose_6)] <- 0
```

Delete participants with missing data on which country they currently live:
```{r, echo= T, results='hide'}
coronadata$country[coronadata$country == ""] <- NA

coronadata <- coronadata %>%
  filter(!is.na(country))
```

Delete participants that are not residents of the country they currently live in:
```{r, echo= T, results='hide'}
coronadata <- coronadata %>%
  filter(countryCitizen == 1)
```

Select baseline data:
```{r baseline data}
coronadataB <- coronadata %>% select(ID, affAnx, affBor, affCalm, affContent, affDepr, affEnerg, affExc, affNerv,
                                     affExh, affInsp, affRel, happy, coronaClose_1, coronaClose_2, coronaClose_3,
                                     coronaClose_4, coronaClose_5, coronaClose_6, countryCitizen, Citizen,
                                     gender, age, country, dateB)
coronadataB<- as_tibble(coronadataB)
head(coronadataB, 5)
```

Select wave 1 data:
```{r wave 1 data}
coronadataW1 <- coronadata %>% select(ID, w1_affAnx, w1_affBor, w1_affCalm, w1_affDepr, w1_affEnerg, w1_affNerv,
                                      w1_affExh, w1_affInsp, w1_affRel, w1_affAng, w1_affLov, w1_coronaClose_1, 
                                      w1_coronaClose_2, w1_coronaClose_3, w1_coronaClose_4, w1_coronaClose_5, 
                                      w1_coronaClose_6, countryCitizen, Citizen, gender, age, country, dateW1)
coronadataW1<- as_tibble(coronadataW1)
head(coronadataW1, 5)
```

Recode oxford data:
```{r, echo= T, results='hide'}
#Recode 
oxforddata$dateB <-anydate(oxforddata$Date)
oxforddata$dateW1 <- anydate(oxforddata$Date)
oxforddata$country <- oxforddata$CountryName
```

Drop not used variables Baseline:
```{r, echo= T, results='hide'}
Stringency_dataB <- oxforddata %>% select(dateB, country, StringencyIndex, ConfirmedCases, ConfirmedDeaths)
```

Drop not used variables W1:
```{r, echo= T, results='hide'}
Stringency_dataW1 <- oxforddata %>% select(dateW1, country, StringencyIndex, ConfirmedCases, ConfirmedDeaths)
```

Join with Baseline data by country and date, rename, and save:
```{r, echo= T, results='hide'}
coronadataBS <- left_join(coronadataB, Stringency_dataB, by=c("country", "dateB"))

coronadataBS <- coronadataBS %>%
  dplyr::rename(
    StringencyIndexB1 = StringencyIndex,
    ConfirmedCasesB1 = ConfirmedCases,
    ConfirmedDeathsB1 = ConfirmedDeaths)

save(coronadataBS, file ="coronadataBS.Rdata")
```

First 10 rows and 8 columns:
```{r}
apa_table(coronadataBS[1:10,1:8])
```

Join with Wave 1 data, rename and save:
```{r, echo= T, results='hide'}
coronadataW1S <- left_join(coronadataW1, Stringency_dataW1, by=c("country", "dateW1"))

coronadataW1S <- coronadataW1S %>%
  dplyr::rename(
    StringencyIndexW1 = StringencyIndex,
    ConfirmedCasesW1 = ConfirmedCases,
    ConfirmedDeathsW1 = ConfirmedDeaths)

save(coronadataW1S, file ="coronadataW1S.Rdata")
```

First 10 rows and 8 columns (still a lot of missing data of participants that only completed baseline):
```{r}
apa_table(coronadataW1S[1:10,1:8])
```

Merge Baseline and W1, drop duplicates, reorder and save:
```{r, echo= T, results='hide'}
coronadataBW1S <- merge(coronadataBS, coronadataW1S, by = "ID")

coronadataBW1S <- coronadataBW1S %>% select(-c(countryCitizen.y, Citizen.y, country.y, gender.y, age.y))

coronadataBW1S <- coronadataBW1S[,c("ID", "dateB", "dateW1", "countryCitizen.x", "Citizen.x", "country.x", "gender.x", "age.x",
                                    "StringencyIndexB1", "StringencyIndexW1", "affAnx", "affBor", "affCalm", "affContent", 
                                    "affDepr", "affEnerg", "affExc", "affNerv", "affExh", "affInsp", "affRel", "happy",
                                     "coronaClose_1", "coronaClose_2", "coronaClose_3", "coronaClose_4", "coronaClose_5", 
                                    "coronaClose_6",
                                     "w1_affAnx", "w1_affBor", "w1_affCalm", "w1_affDepr", "w1_affEnerg", "w1_affNerv",
                                    "w1_affExh", "w1_affInsp", "w1_affRel", "w1_affAng", "w1_affLov", "w1_coronaClose_1", 
                                    "w1_coronaClose_2", "w1_coronaClose_3", "w1_coronaClose_4", "w1_coronaClose_5", 
                                    "w1_coronaClose_6")]

save(coronadataBW1S, file ="coronadataBW1S.Rdata")
```

First 10 rows and 8 columns:
```{r}
apa_table(coronadataBW1S[1:10,1:8])
```

