---
title: "Data preparation for multilevel modeling"
author: "Anne Margit"
date: "07/07/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(dplyr)
library(knitr)
library(lme4)
library(arsenal)
library(lmerTest)
library(tidyverse)
library(anytime)
library(rockchalk)
```

```{r}
load("data_long.Rdata")
oxforddata <- read.csv("OxCGRT_latest.csv", header=TRUE)
```
To check whether country names are different in both datasets:
```{r, echo= T, results='hide'}
levels1 <- levels(data_long$coded_country)
levels2 <- levels(oxforddata$CountryName)

levels1<- as.data.frame(levels1)
levels2<- as.data.frame(levels2)

levels1$levels1 <-as.character(levels1$levels1)
levels2$levels2 <-as.character(levels2$levels2)

check <- comparedf(levels1, levels2, by.x="levels1", by.y="levels2")
summary(check)
```


Some data preparation
```{r rename countries, echo= T, results='hide'}
data_long$coded_country <- 
  plyr::revalue(data_long$coded_country , c("Hong Kong S.A.R."="Hong Kong", 
                                       "Kyrgyzstan" = "Kyrgyz Republic",
                                       "United Republic of Tanzania" = "Tanzania", 
                                       "United States of America" = "United States",
                                       "Republic of Serbia" = "Serbia",
                                       "Slovakia" = "Slovak Republic"))
```

Renaming and recoding variables:
```{r, echo= T, results='hide'}
data_long$age <- as.factor(data_long$age)
names(data_long)[names(data_long) == "coded_country"] <- "Country"
names(data_long)[names(data_long) == "X"] <- "ID"
names(data_long)[names(data_long) == "RecordedDate"] <- "Date"
```

Recoding NA into zero's:
```{r, echo= T, results='hide'}
data_long$Close1[is.na(data_long$Close1)] <- 0
data_long$Close2[is.na(data_long$Close2)] <- 0
data_long$Close3[is.na(data_long$Close3)] <- 0
data_long$Close4[is.na(data_long$Close4)] <- 0
data_long$Close5[is.na(data_long$Close5)] <- 0
data_long$Close6[is.na(data_long$Close6)] <- 0
```

Delete participants with missing data on which country they currently live:
```{r, echo= T, results='hide'}
data_long$Country[data_long$Country == ""] <- NA

data_long <- data_long %>%
  filter(!is.na(Country))
```

Delete participants that are not residents of the country they currently live in:
```{r, echo= T, results='hide'}
data_long <- data_long %>%
  filter(countryCitizen == 1)
```

Delete participants with missing data on age
```{r}
data_long <-data_long %>%
filter(!is.na(age))
```

Delete participants that reported their gender as other or did not provide information:
```{r, echo= T, results='hide'}
data_long <- data_long %>%
  filter(gender == 1 | gender == 2)
```

Recode gender into male = 0 and female = 1
```{r, echo = TRUE, results='hide'}
data_long$gender[data_long$gender == "2"] <- 0
```

Add number of measurements
```{r}
data_long <- data_long %>% group_by(ID) %>% add_tally(wt = !is.na(Date))
```

Filter participants with at least 3 measurements
```{r}
data_long_min3 <- data_long %>% filter(n > 2)
```

```{r}
save(data_long_min3, file="data_long_min3.Rdata")
```

Calculate number of participants per country & select countries with >20 participants:
```{r}
data_long_min3$Country <- as.factor(data_long_min3$Country)
data_long_min3 <- as_tibble(data_long_min3)

Country_N <- data_long_min3 %>%
  filter(Wave == "w0") %>%
  group_by(Country) %>%
  dplyr::summarise(N = n())
```

```{r}
data_long_min3n <- left_join(data_long_min3, Country_N, by="Country")
```

```{r}
data_long_min3_20 <- data_long_min3n %>%
  filter(N>20)
```

```{r}
data_long_min3_20 <- data_long_min3_20 %>%
  select(-Citizen)

summary(data_long_min3_20)
summary(data_long_min3_20$Country)
```

Save
```{r}
save(data_long_min3_20, file="data_long_min3_20.Rdata")
```

Recode oxford data:
```{r, echo= T, results='hide'}
oxforddata$Date <-anydate(oxforddata$Date)
oxforddata$Country <- oxforddata$CountryName
```

Drop not used variables:
```{r, echo= T, results='hide'}
Stringency_data <- oxforddata %>% select(Date, Country, StringencyIndex, ConfirmedCases, ConfirmedDeaths)
```

Impute Stringency Index, fill empty rows with last previously reported index score:
Create new Stringency Index variable first

```{r}
Stringency_data$StringencyIndex_imp <- Stringency_data$StringencyIndex
```

First join, then impute
```{r, echo= T, results='hide'}

data_long_min3_str <- left_join(data_long_min3_20, Stringency_data, by=c("Country", "Date"))

```


Impute
```{r}
data_long_min3_str<-data_long_min3_str[with(data_long_min3_str, order(Country, Date)),]

data_long_min3_str2 <- data_long_min3_str %>%
  group_by(Country) %>%
  fill(StringencyIndex_imp, .direction = "down")

data_long_min3_str <- data_long_min3_str2
```

Check if StringencyIndex and StringencyIndex_imp are identical (they shouldnt be)
```{r}
identical(data_long_min3_str[["StringencyIndex"]],data_long_min3_str[["StringencyIndex_imp"]])
```

Save:
This dataset includes measurements from participants that (1) provided at least 3 measurements, (2) that are residents of the country they currently live in, (3) from countries with at least 20 participants, (4) provided data on age, and (5) with imputed Stringency index values, (6) for baseline through wave 11
```{r}
save(data_long_min3_str, file ="data_long_min3_str.Rdata")
```

Centering Stringency Index
```{r}
data_long_min3_strc <- gmc(data_long_min3_str, "StringencyIndex_imp", "Country", FUN = mean, suffix = c("_mn", "_dev"),
    fulldataframe = TRUE)
```

This dataset also adds the country mean centered stringency index 
```{r}
save(data_long_min3_strc, file="data_long_min3_strc.Rdata")
```


```{r, results = "hide"}
data_means <- data_long_min3_str %>%
    dplyr::group_by(ID) %>%
    dplyr::summarise_each(funs(mean(., na.rm=TRUE)), 
                          Ang, Anxiety, Bored, Calm, Depr, Energ, Exh, Insp, Lov, Nerv, Rel)
```

```{r, results = "hide"}
save(data_means, file="data_means.Rdata")
```
