---
title: "Graphs DaysMax for pooled age groups"
author: "Anne Margit"
date: "8/12/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE}
library(ggplot2)
library(dplyr)
library(knitr)
library(lme4)
library(lmerTest)
library(tidyverse)
library(anytime)
library(rockchalk)
```

This dataset includes measurements from participants that (1) provided at least 3 measurements, (2) that are residents of the country they currently live in, (3) from countries with at least 20 participants, (4) provided data on age, and (5) with imputed Stringency index values that are (6) centered around country means and (7) a variable called DaysMax that indicates the days preceding or leading up to the day on which maximum stringency was reached for the respective country, and (8) from all waves (baseline through wave 11) for (9) the pooled age groups

!!! DaysMax = 0: Day on which maximum stringency was reached for country in which participant lives. This is based on available Stringency Index data, not imputed scores !!!

```{r, results = "hide"}
load("data_long_min3_str_age_max.Rdata")
```

####################### Anxiety #######################

Plot Anxiety and DaysMax for different age groups / LOESS plot (doesn't work well for large datasets? check this)
```{r}
plot_anx <- ggplot(data = data_long_min3_str_age_max, aes(x = DaysMax, y = Anxiety, group = ID, color = age_new))

plot_anx + stat_smooth(aes(group=age_new), se = FALSE, method = "loess", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="LOESS plot of Anxiety by DaysMax for different age groups")
```
GAM plot
```{r}
plot_anx + stat_smooth(aes(group=age_new), se = FALSE, method = "gam", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="GAM plot of Anxiety by DaysMax for different age groups")
```

####################### Anger ####################### 

LOESS plot Anger and DaysMax for different age groups
```{r}
plot_ang <- ggplot(data = data_long_min3_str_age_max, aes(x = DaysMax, y = Ang, group = ID, color = age_new))

plot_ang + stat_smooth(aes(group=age_new), se = FALSE, method = "loess", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="LOESS plot of Anger by DaysMax for different age groups", y ="Anger")
```
GAM plot
```{r}
plot_ang + stat_smooth(aes(group=age_new), se = FALSE, method = "gam", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="GAM plot of Anger by DaysMax for different age groups", y ="Anger")
```

####################### Bored ####################### 
LOESS plot Boredom and DaysMax for different age groups / lot of missing data in Boredom
```{r}
plot_bor <- ggplot(data = data_long_min3_str_age_max, aes(x = DaysMax, y = Bored, group = ID, color = age_new))

plot_bor + stat_smooth(aes(group=age_new), se = FALSE, method = "loess", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="LOESS plot of Boredom by DaysMax for different age groups", y ="Boredom")
```
GAM plot
```{r}
plot_bor + stat_smooth(aes(group=age_new), se = FALSE, method = "gam", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="GAM plot of Boredom by DaysMax for different age groups", y ="Boredom")
```

####################### Calm ####################### 
LOESS plot Calm and DaysMax for different age groups 
```{r}
plot_calm <- ggplot(data = data_long_min3_str_age_max, aes(x = DaysMax, y = Calm, group = ID, color = age_new))

plot_calm + stat_smooth(aes(group=age_new), se = FALSE, method = "loess", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="LOESS plot of Calm by DaysMax for different age groups", y ="Calm")
```

GAM plot
```{r}
plot_calm + stat_smooth(aes(group=age_new), se = FALSE, method = "gam", formula = y ~ x, size = 1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="GAM plot of Calm by DaysMax for different age groups", y ="Calm")
```

####################### Depressed ####################### 
LOESS plot Depressed and DaysMax for different age groups 
```{r}
plot_depr <- ggplot(data = data_long_min3_str_age_max, aes(x = DaysMax, y = Depr, group = ID, color = age_new))

plot_depr + stat_smooth(aes(group=age_new), se = FALSE, method = "loess", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="LOESS plot of Depressed by DaysMax for different age groups", y ="Depr")
```
GAM plot
```{r}
plot_depr + stat_smooth(aes(group=age_new), se = FALSE, method = "gam", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="GAM plot of Depressed by DaysMax for different age groups", y ="Depr")
```

####################### Energetic ####################### 

LOESS plot Energetic and DaysMax for different age groups 
```{r}
plot_energ <- ggplot(data = data_long_min3_str_age_max, aes(x = DaysMax, y = Energ, group = ID, color = age_new))

plot_energ + stat_smooth(aes(group=age_new), se = FALSE, method = "loess", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="LOESS plot of Energetic by DaysMax for different age groups", y ="Energ")
```
GAM plot
```{r}
plot_energ + stat_smooth(aes(group=age_new), se = FALSE, method = "gam", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="GAM plot of Energetic by DaysMax for different age groups", y ="Energ")
```

####################### Exhausted ####################### 

LOESS plot Exhausted and DaysMax for different age groups 
```{r}
plot_exh <- ggplot(data = data_long_min3_str_age_max, aes(x = DaysMax, y = Exh, group = ID, color = age_new))

plot_exh + stat_smooth(aes(group=age_new), se = FALSE, method = "loess", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="LOESS plot of Exhausted by DaysMax for different age groups", y ="Exh")
```
GAM plot
```{r}
plot_exh + stat_smooth(aes(group=age_new), se = FALSE, method = "gam", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="GAM plot of Exhausted by DaysMax for different age groups", y ="Exh")
```

####################### Inspired ####################### 
LOESS plot inspired and DaysMax for different age groups 
```{r}
plot_insp <- ggplot(data = data_long_min3_str_age_max, aes(x = DaysMax, y = Insp, group = ID, color = age_new))

plot_insp + stat_smooth(aes(group=age_new), se = FALSE, method = "loess", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="LOESS plot of Inspired by DaysMax for different age groups", y ="Insp")
```
GAM plot
```{r}
plot_insp + stat_smooth(aes(group=age_new), se = FALSE, method = "gam", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="GAM plot of Inspired by DaysMax for different age groups", y ="Insp")
```

####################### Loved ####################### 

LOESS plot Loved and DaysMax for different age groups 
```{r}
plot_lov <- ggplot(data = data_long_min3_str_age_max, aes(x = DaysMax, y = Lov, group = ID, color = age_new))

plot_lov + stat_smooth(aes(group=age_new), se = FALSE, method = "loess", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="LOESS plot of Loved by DaysMax for different age groups", y ="Lov")
```
GAM plot
```{r}
plot_lov + stat_smooth(aes(group=age_new), se = FALSE, method = "gam", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="GAM plot of Inspired by DaysMax for different age groups", y ="Lov")
```

####################### Nervous ####################### 
LOESS plot Nervous and DaysMax for different age groups 
```{r}
plot_nerv <- ggplot(data = data_long_min3_str_age_max, aes(x = DaysMax, y = Nerv, group = ID, color = age_new))

plot_nerv + stat_smooth(aes(group=age_new), se = FALSE, method = "loess", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="LOESS plot of Nervousness by DaysMax for different age groups", y ="Nerv")
```
GAM plot
```{r}
plot_nerv + stat_smooth(aes(group=age_new), se = FALSE, method = "gam", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="GAM plot of Nervousness by DaysMax for different age groups", y ="Nerv")
```

####################### Relaxed ####################### 
LOESS plot Relaxed and DaysMax for different age groups 
```{r}
plot_rel <- ggplot(data = data_long_min3_str_age_max, aes(x = DaysMax, y = Rel, group = ID, color = age_new))

plot_rel + stat_smooth(aes(group=age_new), se = FALSE, method = "loess", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + labs(title="LOESS plot of Relaxed by DaysMax for different age groups", y ="Rel")
```
GAM plot
```{r}
plot_rel + stat_smooth(aes(group=age_new), se = FALSE, method = "gam", formula = y ~ x, size = 1, na.rm=TRUE) + scale_colour_discrete(name = "Age", 
labels =  c("18-24", "25-44", "45-64", "65+")) + labs(title="GAM plot of Relaxed by DaysMax for different age groups", y ="Rel")
```
