---
title: "Plots of emotion means against stringency or time"
author: "Anne Margit"
date: "8/25/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = F, message=F, warning=F}
library(ggplot2)
library(dplyr)
library(knitr)
library(lme4)
library(lmerTest)
library(tidyverse)
library(anytime)
library(rockchalk)
```

This dataset includes:
1. Participants who provided at least 3 measurements 
2. Participants who are residents of the country they currently live in
3. Participants who provided info on age
4. Participants who provided info on gender (either male or female)
5. Data from countries with at least 20 participants
6. An imputed Stringency index (StringencyIndex_imp) 
7. A variable indicating the number of days before and after the day on which maximum stringency was reached for the respective country (DaysMax)
8. Data from all weekly measurement waves (baseline through wave 11) 
9. Pooled age groups
10. Imputed emotion scores
11. Combined emotion scores (NAA, NAD, PAA, PAD)

!!! DaysMax = 0: Day on which maximum stringency was reached for country in which participant lives. This is based on available Stringency Index data, not imputed scores !!!

```{r, results = "hide"}
load("data_imputed_emomeans.Rdata")
```

# Negative affect high arousal
**Median NAA against date**
```{r, echo=T, message=F, warning=F}
plot_NAA <- ggplot(data_imputed_emomeans, aes(x=Date, y=NAA))

plot_NAA +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5))
```

**Median NAA against wave**
```{r, echo=T, message=F, , warning=F}
plot_NAA <- ggplot(data_imputed_emomeans, aes(x=Time, y=NAA))

plot_NAA +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5))
```

**Median NAA against maximum stringency**
```{r, echo=T, message=F, warning=F}
plot_NAA <- ggplot(data_imputed_emomeans, aes(x=DaysMax, y=NAA))

plot_NAA +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5))
```

**Mean NAA against date in different age groups**
```{r, echo=T, message=F, warning=F}
plot_NAA <- ggplot(data_imputed_emomeans, aes(x=Date, y=NAA, group = Age_new, color = Age_new))

plot_NAA +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+"))
```

**Mean NAA against wave in different age groups**
```{r, echo=T, message=F, warning=F}
plot_NAA <- ggplot(data_imputed_emomeans, aes(x=Time, y=NAA, group = Age_new, color = Age_new))

plot_NAA +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+"))
```

**Mean NAA against maximum stringency in different age groups**
```{r, echo=T, message=F, warning=F}
plot_NAA <- ggplot(data_imputed_emomeans, aes(x=DaysMax, y=NAA, group = Age_new, color = Age_new))

plot_NAA +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+"))
```

# Negative affect low arousal
**Median NAD against date**
```{r, echo=T, message=F, warning=F}
plot_NAD <- ggplot(data_imputed_emomeans, aes(x=Date, y=NAD))

plot_NAD +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5))
```

**Median NAD against wave**
```{r, echo=T, message=F, , warning=F}
plot_NAD <- ggplot(data_imputed_emomeans, aes(x=Time, y=NAD))

plot_NAD +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5))
```

**Median NAD against maximum stringency**
```{r, echo=T, message=F, warning=F}
plot_NAD <- ggplot(data_imputed_emomeans, aes(x=DaysMax, y=NAD))

plot_NAD +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5))
```

**Mean NAD against date in different age groups**
```{r, echo=T, message=F, warning=F}
plot_NAD <- ggplot(data_imputed_emomeans, aes(x=Date, y=NAD, group = Age_new, color = Age_new))

plot_NAD +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+"))
```

**Mean NAD against wave in different age groups**
```{r, echo=T, message=F, warning=F}
plot_NAD <- ggplot(data_imputed_emomeans, aes(x=Time, y=NAD, group = Age_new, color = Age_new))

plot_NAD +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+"))
```

**Mean NAD against maximum stringency in different age groups**
```{r, echo=T, message=F, warning=F}
plot_NAD <- ggplot(data_imputed_emomeans, aes(x=DaysMax, y=NAD, group = Age_new, color = Age_new))

plot_NAD +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+"))
```


# Positive affect high arousal
**Median PAA against date**
```{r, echo=T, message=F, warning=F}
plot_PAA <- ggplot(data_imputed_emomeans, aes(x=Date, y=PAA))

plot_PAA +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5))
```

**Median PAA against wave**
```{r, echo=T, message=F, , warning=F}
plot_PAA <- ggplot(data_imputed_emomeans, aes(x=Time, y=PAA))

plot_PAA +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5))
```

**Median PAA against maximum stringency**
```{r, echo=T, message=F, warning=F}
plot_PAA <- ggplot(data_imputed_emomeans, aes(x=DaysMax, y=PAA))

plot_PAA +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5))
```

**Mean PAA against date in different age groups**
```{r, echo=T, message=F, warning=F}
plot_PAA <- ggplot(data_imputed_emomeans, aes(x=Date, y=PAA, group = Age_new, color = Age_new))

plot_PAA +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+"))
```

**Mean PAA against wave in different age groups**
```{r, echo=T, message=F, warning=F}
plot_PAA <- ggplot(data_imputed_emomeans, aes(x=Time, y=PAA, group = Age_new, color = Age_new))

plot_PAA +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+"))
```

**Mean PAA against maximum stringency in different age groups**
```{r, echo=T, message=F, warning=F}
plot_PAA <- ggplot(data_imputed_emomeans, aes(x=DaysMax, y=PAA, group = Age_new, color = Age_new))

plot_PAA +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+"))
```

# Positive affect low arousal
**Median PAD against date**
```{r, echo=T, message=F, warning=F}
plot_PAD <- ggplot(data_imputed_emomeans, aes(x=Date, y=PAD))

plot_PAD +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5))
```

**Median PAD against wave**
```{r, echo=T, message=F, , warning=F}
plot_PAD <- ggplot(data_imputed_emomeans, aes(x=Time, y=PAD))

plot_PAD +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5))
```

**Median PAD against maximum stringency**
```{r, echo=T, message=F, warning=F}
plot_PAD <- ggplot(data_imputed_emomeans, aes(x=DaysMax, y=PAD))

plot_PAD +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5))
```

**Mean PAD against date in different age groups**
```{r, echo=T, message=F, warning=F}
plot_PAD <- ggplot(data_imputed_emomeans, aes(x=Date, y=PAD, group = Age_new, color = Age_new))

plot_PAD +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+"))
```

**Mean PAD against wave in different age groups**
```{r, echo=T, message=F, warning=F}
plot_PAD <- ggplot(data_imputed_emomeans, aes(x=Time, y=PAD, group = Age_new, color = Age_new))

plot_PAD +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+"))
```

**Mean PAD against maximum stringency in different age groups**
```{r, echo=T, message=F, warning=F}
plot_PAD <- ggplot(data_imputed_emomeans, aes(x=DaysMax, y=PAD, group = Age_new, color = Age_new))

plot_PAD +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+"))
```




