---
title: "Plots of emotion means against stringency or time in weeks"
author: "Anne Margit"
date: "8/25/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = F, message=F, warning=F}
library(ggplot2)
library(dplyr)
library(knitr)
library(lme4)
library(lmerTest)
library(tidyverse)
library(anytime)
library(rockchalk)
```

This dataset includes:

1. Data from all weekly measurement waves (baseline through wave 11, Time 1 through 12) 
2. Participants who provided at least 3 measurements 
3. Participants who are residents of the country they currently live in
4. Participants who provided info on age
5. Participants who provided info on gender (either male or female)
6. Data from countries with at least 20 participants
7. Pooled age groups
8. Imputed missing emotion scores
9. Combined emotion scores (NAA, NAD, PAA, PAD)
10. An imputed Stringency index (StringencyIndex_imp) 
11. A variable indicating the number of days before and after the day on which maximum stringency was reached for the respective country (DaysMax)
12. A variable indicating the number of weeks before and after the day on which maximum stringency was reached for the respective country (WeeksMax)
13. A variable indicating the date on which maximum Stringency was reached for that country (DateMaxStr)

```{r, results = "hide"}
load("data_imputed_emomeans_maxweeks.Rdata")
```

# Negative affect high arousal
**Median NAA against week**
```{r, echo=T, message=F, warning=F}
plot_NAA <- ggplot(data_imputed_emomeans_maxweeks, aes(x=Week, y=NAA))

plot_NAA +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5)) + ylim(1,5) + xlim(10,26)
```

**Median NAA against maximum stringency in weeks**
```{r, echo=T, message=F, warning=F}
plot_NAA <- ggplot(data_imputed_emomeans_maxweeks, aes(x=WeeksMax, y=NAA))

plot_NAA +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5)) + ylim(1,5) + xlim(-10, 15)
```

**Mean NAA against week in different age groups**
```{r, echo=T, message=F, warning=F}
plot_NAA <- ggplot(data_imputed_emomeans_maxweeks, aes(x=Week, y=NAA, group = Age_new, color = Age_new))

plot_NAA +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + ylim(1,5) + xlim(10,26)
```

**Mean NAA against maximum stringency in weeks in different age groups**
```{r, echo=T, message=F, warning=F}
plot_NAA <- ggplot(data_imputed_emomeans_maxweeks, aes(x=WeeksMax, y=NAA, group = Age_new, color = Age_new))

plot_NAA +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + ylim(1,5) + xlim(-10, 15)
```

# Negative affect low arousal
**Median NAD against week**
```{r, echo=T, message=F, warning=F}
plot_NAD <- ggplot(data_imputed_emomeans_maxweeks, aes(x=Week, y=NAD))

plot_NAD +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5)) + ylim(1,5) + xlim(10,26)
```

**Median NAD against maximum stringency in weeks**
```{r, echo=T, message=F, warning=F}
plot_NAD <- ggplot(data_imputed_emomeans_maxweeks, aes(x=WeeksMax, y=NAD))

plot_NAD +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5)) + ylim(1,5) + xlim(-10, 15)
``` 

**Mean NAD against week in different age groups**
```{r, echo=T, message=F, warning=F}
plot_NAD <- ggplot(data_imputed_emomeans_maxweeks, aes(x=Week, y=NAD, group = Age_new, color = Age_new))

plot_NAD +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + ylim(1,5) + xlim(10,26)
```

**Mean NAD against maximum stringency in weeks in different age groups**
```{r, echo=T, message=F, warning=F}
plot_NAD <- ggplot(data_imputed_emomeans_maxweeks, aes(x=WeeksMax, y=NAD, group = Age_new, color = Age_new))

plot_NAD +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + ylim(1,5) + xlim(-10, 15)
```


# Positive affect high arousal
**Median PAA against week**
```{r, echo=T, message=F, warning=F}
plot_PAA <- ggplot(data_imputed_emomeans_maxweeks, aes(x=Week, y=PAA))

plot_PAA +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5)) + ylim(1,5) + xlim(10, 26)
```

**Median PAA against maximum stringency in weeks**
```{r, echo=T, message=F, warning=F}
plot_PAA <- ggplot(data_imputed_emomeans_maxweeks, aes(x=WeeksMax, y=PAA))

plot_PAA +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5)) + ylim(1,5) + xlim(-10, 15)
```

**Mean PAA against week in different age groups**
```{r, echo=T, message=F, warning=F}
plot_PAA <- ggplot(data_imputed_emomeans_maxweeks, aes(x=Week, y=PAA, group = Age_new, color = Age_new))

plot_PAA +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + ylim(1,5) + xlim(10, 26)
```

**Mean PAA against maximum stringency in different age groups**
```{r, echo=T, message=F, warning=F}
plot_PAA <- ggplot(data_imputed_emomeans_maxweeks, aes(x=WeeksMax, y=PAA, group = Age_new, color = Age_new))

plot_PAA +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + ylim(1,5) + xlim(-10, 15)
```

# Positive affect low arousal
**Median PAD against week**
```{r, echo=T, message=F, warning=F}
plot_PAD <- ggplot(data_imputed_emomeans_maxweeks, aes(x=Week, y=PAD))

plot_PAD +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5)) + ylim(1,5) + xlim(10, 26)
```

**Median PAD against maximum stringency**
```{r, echo=T, message=F, warning=F}
plot_PAD <- ggplot(data_imputed_emomeans_maxweeks, aes(x=WeeksMax, y=PAD))

plot_PAD +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5)) + ylim(1,5) + xlim(-10,15)
```

**Mean PAD against week in different age groups**
```{r, echo=T, message=F, warning=F}
plot_PAD <- ggplot(data_imputed_emomeans_maxweeks, aes(x=Week, y=PAD, group = Age_new, color = Age_new))

plot_PAD +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + ylim(1,5) + xlim(10,26)
```

**Mean PAD against maximum stringency in different age groups**
```{r, echo=T, message=F, warning=F}
plot_PAD <- ggplot(data_imputed_emomeans_maxweeks, aes(x=WeeksMax, y=PAD, group = Age_new, color = Age_new))

plot_PAD +  stat_summary(geom = "line", fun = mean, size=1) + scale_colour_discrete(name = "Age", 
labels = c("18-24", "25-44", "45-64", "65+")) + ylim(1,5) + xlim(-10,15)
```




