---
title: "200812 Descriptives pooled age groups"
author: "Anne Margit"
date: "08/12/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(tidyverse)
library(stringr)
library(papaja)
library(ggpubr)
library(ggplot2)
```

Descriptive statistics
This dataset includes measurements from participants that (1) provided at least 3 measurements, (2) that are residents of the country they currently live in, (3) from countries with at least 20 participants, (4) provided data on age, combined with imputed Stringency Index (5) pooled age groups

```{r}
load("data_long_min3_str_age.Rdata")
load("data_means.Rdata")
```

How much missing data is left?
```{r, results = "hide"}
#Missing data
missing.values <- data_long_min3_str_age %>%
  gather(key = "key", value = "val") %>%
  dplyr::mutate(is.missing = is.na(val)) %>%
  dplyr::group_by(key, is.missing) %>%
  dplyr::summarise(num.missing = n()) %>%
  dplyr::filter(is.missing==T) %>%
  dplyr::select(-is.missing) %>%
  dplyr::arrange(desc(num.missing))

```

```{r}
apa_table(missing.values)
```

Number of participants per country
```{r, results = "hide"}
data_long_min3_str_age$Country <- as.factor(data_long_min3_str_age$Country)

Country_N <- data_long_min3_str_age %>%
  filter(Wave == "w0") %>%
  group_by(Country) %>%
  summarise(NCountry = n())
```

```{r}
apa_table(Country_N)
```

Number of measurements per wave, emotion measurements per wave, and Stringency Index measurements per wave

```{r, results = "hide"}
data_long_min3_str_age$Wave <- as.factor(data_long_min3_str_age$Wave)

Wave_N <- data_long_min3_str_age %>% 
group_by(Wave)%>%
summarise(NWave = sum (!is.na(Date)), NAng= sum(!is.na(Ang)), NAnx= sum(!is.na(Anxiety)), NBored= sum(!is.na(Bored)), NCalm= sum(!is.na(Calm)),
NDepr= sum(!is.na(Depr)), NEnerg= sum(!is.na(Energ)), NExh= sum(!is.na(Exh)), NInsp= sum(!is.na(Insp)), NLov= sum(!is.na(Lov)), NNerv= sum(!is.na(Nerv)), NRel= sum(!is.na(Rel)), NStr = sum(!is.na(StringencyIndex)))
```

```{r}
apa_table(Wave_N)
```

Number of participants per age group

```{r, results = "hide"}
data_long_min3_str_age$age <- as.factor(data_long_min3_str_age$age)

Age_N <- data_long_min3_str_age %>%
  filter(Wave=="w0") %>%
  group_by(age) %>%
  summarise(NAge = n())
```

Number of participants per pooled age group

```{r, results = "hide"}
data_long_min3_str_age$age_new <- as.factor(data_long_min3_str_age$age_new)

Age_New <- data_long_min3_str_age %>%
  filter(Wave=="w0") %>%
  group_by(age_new) %>%
  summarise(NAge = n())
```
```{r}
apa_table(Age_N)
```

```{r}
apa_table(Age_New)
```

Number of males and females per age group     
```{r, results = "hide"}
Age_Gender <- data_long_min3_str_age %>%
  filter(Wave == "w0") %>%
  select(age, gender) %>%
  group_by(age, gender) %>%
  count(gender)
```
Number of males and females per pooled age group     
```{r, results = "hide"}
Age_New_Gender <- data_long_min3_str_age %>%
  filter(Wave == "w0") %>%
  select(age_new, gender) %>%
  group_by(age_new, gender) %>%
  count(gender)
```

Note: Age 1 = 18-24, 2 = 25-34, 3 = 35-44, 4 = 45-54, 5 = 55-64, 6 = 65-74, 7 = 75-85, 8 = 85+     
Gender: 1 = Female, 2 = Male, 3 = Other
```{r}
apa_table(Age_Gender)
```

0 = male, 1 = female
```{r}
apa_table(Age_New_Gender)
```

Mean and SD, minimum and maximum of Stringency Index per country
```{r, results = "hide"}
StringencySummary <- data_long_min3_str_age %>%
  group_by(Country)%>%
  summarize(mean = mean(StringencyIndex, na.rm=TRUE), sd = sd(StringencyIndex, na.rm=TRUE), 
            max = max(StringencyIndex, na.rm=TRUE), min = min(StringencyIndex, na.rm=TRUE))
```

```{r}
apa_table(StringencySummary)
```

```{r, results = "hide"}
data_means2 <- data_means %>%
dplyr::rename(Ang_mean = Ang,
Axiety_mean = Anxiety,
Bored_mean = Bored,
Calm_mean = Calm,
Depr_mean = Depr,
Energ_mean = Energ,
Exh_mean = Exh,
Insp_mean = Insp,
Lov_mean = Lov,
Nerv_mean = Nerv,
Rel_mean = Rel)

data_graphs<- left_join(data_long_min3_str_age, data_means2, by="ID")
```
The dataframe data_graphs contains both raw scores and participant mean scores, mean scores have the addition "_mean"

Plotting raw data


Boxplots
```{r, results = "hide"}
theme_set(theme_classic())

gb_anx <- ggplot(data_graphs, aes(age_new, Anxiety)) + geom_boxplot(varwidth=T, aes(fill= age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_ang <- ggplot(data_graphs, aes(age_new, Ang)) + geom_boxplot(varwidth=T, aes(fill= age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_bor <- ggplot(data_graphs, aes(age_new, Bored)) + geom_boxplot(varwidth=T, aes(fill= age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_depr <- ggplot(data_graphs, aes(age_new, Depr)) + geom_boxplot(varwidth=T, aes(fill= age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_exh <- ggplot(data_graphs, aes(age_new, Exh)) + geom_boxplot(varwidth=T, aes(fill= age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_nerv <- ggplot(data_graphs, aes(age_new, Nerv)) + geom_boxplot(varwidth=T, aes(fill= age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_calm <- ggplot(data_graphs, aes(age_new, Calm)) + geom_boxplot(varwidth=T, aes(fill= age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_energ <- ggplot(data_graphs, aes(age_new, Energ)) + geom_boxplot(varwidth=T, aes(fill= age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_insp <- ggplot(data_graphs, aes(age_new, Insp)) + geom_boxplot(varwidth=T, aes(fill= age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_lov <- ggplot(data_graphs, aes(age_new, Lov)) + geom_boxplot(varwidth=T, aes(fill= age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_rel <- ggplot(data_graphs, aes(age_new, Rel)) + geom_boxplot(varwidth=T, aes(fill= age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_NA <- ggarrange(gb_anx, gb_ang, gb_bor, gb_depr, gb_exh, gb_nerv, ncol = 3, nrow = 2, common.legend= TRUE, legend = "bottom")

gb_PA <- ggarrange(gb_calm, gb_energ, gb_insp, gb_lov, gb_rel, ncol = 3, nrow = 2, common.legend= TRUE, legend = "bottom")
```
```{r}
gb_NA
gb_PA
```

Histograms NA
```{r, results = "hide"}
g_anx <- ggplot(data_graphs, aes(x=Anxiety, fill=age_new)) + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_ang <- ggplot(data_graphs, aes(x=Ang, fill=age_new)) + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_bor <- ggplot(data_graphs, aes(x=Bored, fill=age_new)) + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_dep <- ggplot(data_graphs, aes(x=Depr, fill=age_new)) + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_exh <- ggplot(data_graphs, aes(x=Exh, fill=age_new)) + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_nerv <- ggplot(data_graphs, aes(x=Nerv, fill=age_new)) + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_calm <- ggplot(data_graphs, aes(x=Calm, fill=age_new)) + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_energ <- ggplot(data_graphs, aes(x=Energ, fill=age_new))  + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_insp <- ggplot(data_graphs, aes(x=Insp, fill=age_new))  + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_lov <- ggplot(data_graphs, aes(x=Lov, fill=age_new))  + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_rel <- ggplot(data_graphs, aes(x=Rel, fill=age_new))  + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gh_NA <- ggarrange(g_anx, g_ang, g_bor, g_dep, g_exh, g_nerv, ncol = 3, nrow = 2, common.legend= TRUE, legend = "bottom")

gh_PA <- ggarrange(g_calm, g_energ, g_insp, g_lov, g_rel, ncol = 3, nrow = 2, common.legend= TRUE, legend = "bottom")
```

```{r}
gh_NA
gh_PA
```

Stringency plots
```{r, results = "hide"}
data_graphs$Country <- as.character(data_graphs$Country)

data_graphs1 <- data_graphs %>%
filter(Country == "Argentina" |  Country == "Australia" | Country == "Brazil" | Country == "Canada" | Country == "Chile" 
       | Country == "Croatia" | Country == "France" | Country == "Germany" )

data_graphs2 <- data_graphs %>%
filter(Country == "Greece" | Country == "Hungary" | Country == "Indonesia" | Country == "Italy" | Country == "Japan" | Country == "Kazakhstan" | Country == "Kosovo" | Country == "Malaysia" )

data_graphs3 <- data_graphs %>%
filter(Country == "Netherlands" | Country == "Peru" | Country == "Philippines" | Country == "Poland" | Country == "Serbia" | Country == "Romania" |
         Country == "Russia" | Country == "Saudi Arabia")

data_graphs4 <- data_graphs %>%
filter(Country == "Singapore" | Country == "South Africa" | Country == "South Korea" | Country == "Spain" 
       | Country == "Turkey" | Country == "Ukraine" | Country == "United Kingdom" | Country == "United States" | Country == "Vietnam")

g_s1 <- ggplot(data_graphs1, aes(StringencyIndex, Country)) + geom_violin(aes(fill=factor(Country)))

g_s2 <- ggplot(data_graphs2, aes(StringencyIndex, Country)) + geom_violin(aes(fill=factor(Country)))

g_s3 <- ggplot(data_graphs3, aes(StringencyIndex, Country)) + geom_violin(aes(fill=factor(Country)))

g_s4 <- ggplot(data_graphs4, aes(StringencyIndex, Country)) + geom_violin(aes(fill=factor(Country)))

```

```{r}
g_s1
g_s2
g_s3
g_s4
```


