---
title: "200822 Descriptives pooled age groups"
author: "Anne Margit"
date: "08/22/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=F}
library(dplyr)
library(tidyverse)
library(stringr)
library(papaja)
library(ggpubr)
library(ggplot2)
```

Descriptive statistics
This dataset includes measurements from participants that (1) provided at least 3 measurements, (2) that are residents of the country they currently live in, (3) from countries with at least 20 participants, (4) provided data on age, combined with imputed Stringency Index (5) pooled age groups

```{r}
load("data_long_min3_str_age.Rdata")
```

How much missing data is left?
```{r, results = "hide", message=F}
#Missing data
missing.values <- data_long_min3_str_age %>%
  gather(key = "key", value = "val") %>%
  dplyr::mutate(is.missing = is.na(val)) %>%
  dplyr::group_by(key, is.missing) %>%
  dplyr::summarise(num.missing = n()) %>%
  dplyr::filter(is.missing==T) %>%
  dplyr::select(-is.missing) %>%
  dplyr::arrange(desc(num.missing))

```

```{r}
apa_table(missing.values, caption="Missing data")
```

Number of participants per country on baseline 
```{r, results = "hide", message=F}
data_long_min3_str_age$Country <- as.factor(data_long_min3_str_age$Country)

Country_N <- data_long_min3_str_age %>%
  filter(Time == "1") %>%
  group_by(Country) %>%
  summarise(NCountry = n())
```

```{r}
apa_table(Country_N, caption = "Number of participants per country on baseline")
```

Number of measurements per wave, emotion measurements per wave, and Stringency Index measurements per wave
```{r, results = "hide", message=F}
data_long_min3_str_age$Time <- as.factor(data_long_min3_str_age$Time)

Wave_N <- data_long_min3_str_age %>% 
group_by(Time)%>%
summarise(NWave = sum (!is.na(Date)), NAng= sum(!is.na(Ang)), NAnx= sum(!is.na(Anxiety)), NNerv= sum(!is.na(Nerv)), NDepr= sum(!is.na(Depr)), NExh= sum(!is.na(Exh)), NEnerg= sum(!is.na(Energ)),  NInsp= sum(!is.na(Insp)), NCalm= sum(!is.na(Calm)), NRel= sum(!is.na(Rel)), NStr = sum(!is.na(StringencyIndex)))
```

```{r}
apa_table(Wave_N, caption="Number of measurements per wave")
```

Number of participants per age group on baseline
```{r, results = "hide", message=F}
data_long_min3_str_age$Age <- as.factor(data_long_min3_str_age$Age)

Age_N <- data_long_min3_str_age %>%
  filter(Time=="1") %>%
  group_by(Age) %>%
  summarise(NAge = n())
```
```{r}
apa_table(Age_N, caption="Number of participants per age group on baseline")
```

Number of participants per pooled age group
```{r, results = "hide", message=F}
data_long_min3_str_age$Age_new <- as.factor(data_long_min3_str_age$Age_new)

Age_New <- data_long_min3_str_age %>%
  filter(Time=="1") %>%
  group_by(Age_new) %>%
  summarise(NAge = n())
```

```{r}
apa_table(Age_New, caption="Number of participants per pooled age group on baseline")
```

Number of males and females per age group on baseline     
```{r, results = "hide", message=F}
Age_Gender <- data_long_min3_str_age %>%
  filter(Time == "1") %>%
  select(Age, Gender) %>%
  group_by(Age, Gender) %>%
  count(Gender)
```
```{r}
apa_table(Age_Gender, caption="Number of males and females per age group on baseline", note="Age 1= 18-24; 2= 25-34; 3= 35-44; 4= 45-54; 5= 55-64; 6= 65-74; 7= 75-84; 8=85+; Gender 0= male; 1= female")
```

Number of males and females per pooled age group on baseline   
```{r, results = "hide", message=F}
Age_New_Gender <- data_long_min3_str_age %>%
  filter(Time == "1") %>%
  select(Age_new, Gender) %>%
  group_by(Age_new, Gender) %>%
  count(Gender)
```
 
```{r}
apa_table(Age_New_Gender, caption = "Number of males and females per pooled age group on baseline",
          note= "Age 0= 18-24; 1= 25-44; 2= 45-64; 3= 65+, Gender 0= male; 1= female")
```

Mean and SD, minimum and maximum of Stringency Index per country
```{r, results = "hide", message=F}
StringencySummary <- data_long_min3_str_age %>%
  group_by(Country)%>%
  summarize(mean = mean(StringencyIndex, na.rm=TRUE), sd = sd(StringencyIndex, na.rm=TRUE), 
            max = max(StringencyIndex, na.rm=TRUE), min = min(StringencyIndex, na.rm=TRUE))
```

```{r}
apa_table(StringencySummary, caption="Stringency Index per country")
```

Boxplots
```{r, results = "hide", message=F, warning=F}
theme_set(theme_classic())

gb_anx <- ggplot(data_long_min3_str_age, aes(Age_new, Anxiety)) + geom_boxplot(varwidth=T, aes(fill= Age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_ang <- ggplot(data_long_min3_str_age, aes(Age_new, Ang)) + geom_boxplot(varwidth=T, aes(fill= Age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_nerv <- ggplot(data_long_min3_str_age, aes(Age_new, Nerv)) + geom_boxplot(varwidth=T, aes(fill= Age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_depr <- ggplot(data_long_min3_str_age, aes(Age_new, Depr)) + geom_boxplot(varwidth=T, aes(fill= Age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_exh <- ggplot(data_long_min3_str_age, aes(Age_new, Exh)) + geom_boxplot(varwidth=T, aes(fill= Age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_energ <- ggplot(data_long_min3_str_age, aes(Age_new, Energ)) + geom_boxplot(varwidth=T, aes(fill= Age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_insp <- ggplot(data_long_min3_str_age, aes(Age_new, Insp)) + geom_boxplot(varwidth=T, aes(fill= Age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_calm <- ggplot(data_long_min3_str_age, aes(Age_new, Calm)) + geom_boxplot(varwidth=T, aes(fill= Age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_rel <- ggplot(data_long_min3_str_age, aes(Age_new, Rel)) + geom_boxplot(varwidth=T, aes(fill= Age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_NA <- ggarrange(gb_anx, gb_ang, gb_depr, gb_exh, gb_nerv, ncol = 3, nrow = 2, common.legend= TRUE, legend = "bottom")

gb_PA <- ggarrange(gb_calm, gb_energ, gb_insp, gb_rel, ncol = 3, nrow = 2, common.legend= TRUE, legend = "bottom")
```

```{r, warning=F}
gb_NA
gb_PA
```

Histograms NA
```{r, results = "hide", message=F, warning=F}
g_anx <- ggplot(data_long_min3_str_age, aes(x=Anxiety, fill=Age_new)) + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_ang <- ggplot(data_long_min3_str_age, aes(x=Ang, fill=Age_new)) + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_nerv <- ggplot(data_long_min3_str_age, aes(x=Nerv, fill=Age_new)) + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_dep <- ggplot(data_long_min3_str_age, aes(x=Depr, fill=Age_new)) + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_exh <- ggplot(data_long_min3_str_age, aes(x=Exh, fill=Age_new)) + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_energ <- ggplot(data_long_min3_str_age, aes(x=Energ, fill=Age_new))  + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_insp <- ggplot(data_long_min3_str_age, aes(x=Insp, fill=Age_new))  + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_calm <- ggplot(data_long_min3_str_age, aes(x=Calm, fill=Age_new)) + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_rel <- ggplot(data_long_min3_str_age, aes(x=Rel, fill=Age_new))  + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gh_NA <- ggarrange(g_anx, g_ang, g_dep, g_exh, g_nerv, ncol = 3, nrow = 2, common.legend= TRUE, legend = "bottom")

gh_PA <- ggarrange(g_calm, g_energ, g_insp, g_rel, ncol = 3, nrow = 2, common.legend= TRUE, legend = "bottom")
```

```{r, warning=F}
gh_NA
gh_PA
```

Stringency plots
```{r, results = "hide", message=F, warning=F}
data_long_min3_str_age$Country <- as.character(data_long_min3_str_age$Country)

data_graphs1 <- data_long_min3_str_age %>%
filter(Country == "Argentina" |  Country == "Australia" | Country == "Brazil" | Country == "Canada" | Country == "Chile" 
       | Country == "Croatia" | Country == "France" | Country == "Germany" )

data_graphs2 <- data_long_min3_str_age %>%
filter(Country == "Greece" | Country == "Hungary" | Country == "Indonesia" | Country == "Italy" | Country == "Japan" | Country == "Kazakhstan" | Country == "Kosovo" | Country == "Malaysia" )

data_graphs3 <- data_long_min3_str_age %>%
filter(Country == "Netherlands" | Country == "Peru" | Country == "Philippines" | Country == "Poland" | Country == "Serbia" | Country == "Romania" |
         Country == "Russia" | Country == "Saudi Arabia")

data_graphs4 <- data_long_min3_str_age %>%
filter(Country == "Singapore" | Country == "South Africa" | Country == "South Korea" | Country == "Spain" 
       | Country == "Turkey" | Country == "Ukraine" | Country == "United Kingdom" | Country == "United States" | Country == "Vietnam")

g_s1 <- ggplot(data_graphs1, aes(StringencyIndex, Country)) + geom_violin(aes(fill=factor(Country)))

g_s2 <- ggplot(data_graphs2, aes(StringencyIndex, Country)) + geom_violin(aes(fill=factor(Country)))

g_s3 <- ggplot(data_graphs3, aes(StringencyIndex, Country)) + geom_violin(aes(fill=factor(Country)))

g_s4 <- ggplot(data_graphs4, aes(StringencyIndex, Country)) + geom_violin(aes(fill=factor(Country)))

```

```{r, warning=F}
g_s1
g_s2
g_s3
g_s4
```


