---
title: "Second analyses NAA Phase 2"
author: "Anne Margit"
date: "9/29/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, set-options, echo=FALSE, cache= FALSE}
options(width=1000)
Sys.getenv('R_MAX_VSIZE')
```

```{r, results = "hide"}
load("data_analyse2_p2.Rdata")
```

This dataset includes:

1. Data from all weekly measurement waves (baseline through wave 11, Time 1 through 12) 
2. Participants who provided at least 3 measurements 
3. Participants who are residents of the country they currently live in
4. Participants who provided info on age
5. Participants who provided info on gender (either male or female)
6. Data from countries with at least 20 participants
7. Pooled age groups
8. Imputed missing emotion scores
9. Combined emotion scores (NAA, NAD, PAA, PAD)
10. An imputed Stringency index (StringencyIndex_imp) 
11. A variable indicating the number of days before and after the day on which maximum stringency was reached for the respective country (DaysMax)
12. A variable indicating the number of weeks before and after the day on which maximum stringency was reached for the respective country (WeeksMax)
13. A variable indicating the date on which maximum Stringency was reached for that country (DateMaxStr)
14. A dummy Str_dummy with 0 = before the peaj, 1 = during peak, 2 = after peak
15. Observations during which there was a second peak are excluded (N=583) 

> My comments are in block quotes such as this. 

```{r, message=F}
library(dplyr)
library(tidyverse)
library(papaja)
library(ggpubr)
library(ggplot2)
library(rockchalk)
library(effects)
library(nlme)
library(lattice)
library(broom)
library(purrr)
```

# Regression models phase 2

**Negative affect high arousal**

*Predictors: DaysMax_p2, Age, Random: IC for Country*
```{r, message=F, comment=NA}
model_NAA1 <- lme(fixed = NAA ~ DaysMax_p2 + Age_new + DaysMax_p2*Age_new,
                   random = ~1 | Country, 
                  data = data_analyse2_p2, 
                  na.action = na.omit)

summary(model_NAA1)
```

*Predictors: DaysMax_p1, Age, Random: IC for ID*
```{r, message=F, comment=NA}
model_NAA2 <- lme(fixed = NAA ~ DaysMax_p2 + Age_new + DaysMax_p2*Age_new,
                  random = ~1 | ID, 
                 data = data_analyse2_p2, 
                 na.action = na.omit)

summary(model_NAA2)
```

*Random: IC for ID and Country*
```{r, message=F, comment=NA}
model_NAA3 <- lme(fixed = NAA ~ DaysMax_p2 + Age_new + DaysMax_p2*Age_new,
                  random = ~1 | Country/ID, 
                  data = data_analyse2_p2, 
                  na.action = na.omit)

summary(model_NAA3)
```

*Random: IC for ID and Country, S for Country*
```{r, message=F, comment=NA}
model_NAA4 <- lme(fixed = NAA ~ DaysMax_p2 + Age_new + DaysMax_p2*Age_new,
                  random = list (Country = ~DaysMax_p2, ID = ~1), 
                  data = data_analyse2_p2, 
                  na.action = na.omit)

summary(model_NAA4)
```

*Random: IC for ID and Country, S for ID*
```{r, message=F, comment=NA}
model_NAA5 <- lme(fixed = NAA ~ DaysMax_p2 + Age_new + DaysMax_p2*Age_new,
                  random = list (Country = ~1, ID = ~DaysMax_p2), 
                  data = data_analyse2_p2, 
                  na.action = na.omit)

summary(model_NAA5)
```

*Random slope for Country and ID*
```{r, message=F, comment=NA}
model_NAA6 <- lme(fixed = NAA ~ DaysMax_p2 + Age_new + DaysMax_p2*Age_new,
                  random = ~DaysMax_p2 | Country/ID, 
                  data = data_analyse2_p2, 
                  na.action = na.omit)

summary(model_NAA6)
```

> Model with random slopes for Country and ID is better  

*Random: IC for ID and Country, S for Country, No correlation between IC and S for Country*
```{r, message=F, comment=NA}
model_NAA7 <- lme(fixed = NAA ~ DaysMax_p2 + Age_new + DaysMax_p2*Age_new,
                  random = list(Country = pdDiag(~DaysMax_p2), ID = ~1), 
                  data = data_analyse2_p2, 
                  na.action = na.omit)

summary(model_NAA7)
```

*Random: IC for ID and Country, S for ID and Country, No correlation between IC and S for Country*
```{r, message=F, comment=NA}
model_NAA8 <- lme(fixed = NAA ~ DaysMax_p2 + Age_new + DaysMax_p2*Age_new,
                  random = list(Country = pdDiag(~DaysMax_p2), ID = ~DaysMax_p2), 
                  data = data_analyse2_p2, 
                  na.action = na.omit)

summary(model_NAA8)
```

*Random: IC for ID and Country, S for ID and Country, No correlation between IC and S for Country and ID*
```{r, message=F, comment=NA}
model_NAA9 <- lme(fixed = NAA ~ DaysMax_p2 + Age_new + DaysMax_p2*Age_new,
                  random = list (Country = pdDiag(~DaysMax_p2), ID = pdDiag(~DaysMax_p2)),
                  data = data_analyse2_p2, 
                  na.action = na.omit)

summary(model_NAA9)
```

> Best model is NAA8: random IC for ID and Country + S for Country and ID + no correlation between IC and S for Country*

*Autoregressive correlation structure for measurements*
```{r, message=F, comment=NA}
data_analyse2_p2 <- data_analyse2_p2[with(data_analyse2_p2, order(Country, ID, Time)),]
data_analyse2_p2$Time <- as.numeric(data_analyse2_p2$Time)

model_NAA10 <- lme(fixed = NAA ~ DaysMax_p2 + Age_new + DaysMax_p2*Age_new,
                  random = list(Country = pdDiag(~DaysMax_p2), ID = ~DaysMax_p2),  
                  data = data_analyse2_p2, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_NAA10)
```

> Model NAA10 has the best fit (lowest BIC). Random intercept for ID and Country, random slope for Country and ID, no correlation between random intercept and slope for Country, AR correlation structure at Measuement level


*QQ plot of residuals*
```{r, message=F, comment=NA}
par(mfrow = c(1,2))
lims <- c(-3.5,3.5)
hist(resid(model_NAA10, type = "normalized"),
freq = FALSE, xlim = lims, ylim =  c(0,.7),main = "Histogram of Standardized Residuals")
lines(density(scale(resid(model_NAA10))))
qqnorm(resid(model_NAA10, type = "normalized"),
xlim = lims, ylim = lims,main = "QQ plot")
abline(0,1, col = "red", lty = 2)
```

*Residuals vs fitted*
```{r, message=F, comment=NA}
plot(fitted(model_NAA10, level=2), residuals(model_NAA10, level=2), 
     main="residuals vs fitted at ID level")
abline(a=0, b=0,col="red")
plot(fitted(model_NAA10, level=1), residuals(model_NAA10, level=1), 
    main="residuals vs fitted at Country level")
abline(a=0, b=0,col="red")
```

> Residuen zien er allemaal goed uit

*Plot random intercepts and slopes*
```{r, message=F, comment=NA}
plot(ranef(model_NAA10, level = 1))
plot(ranef(model_NAA10, level = 2))
```

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_NAA10)
```
*Plot of predicted values*
```{r, results = "hide", message=F}
ef_NAA <- effect("DaysMax_p2:Age_new", model_NAA10)

plot_NAA <- ggplot(as.data.frame(ef_NAA), 
       aes(DaysMax_p2, fit, color=Age_new)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_bw(base_size=12) + scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_NAA
```

```{r, message=F, comment=NA}
coef_NAA = tidy(model_NAA10, 
               effects = "fixed")
```

*Effect sizes*
**Within person SD and average within person SD**
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p2 %>% 
  group_by(ID) %>%
  summarize_at(c("DaysMax_p2", "NAA"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("DaysMax_p2", "NAA"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect size = (regression coefficient * average ISD of X) / average ISD of Y) 

> For the intercept and the dummy variables (+ interaction) I only standardized Y, so the effect size = (regression coefficient / average ISD of Y)

```{r, message=F, comment=NA}
coef_NAA <- coef_NAA %>%
 left_join(., ISDs_av, by=c("term"="ind"))

coef_NAA <- coef_NAA %>%
  mutate(sd = ifelse(is.na(sd), 1, sd))

coef_NAA <- coef_NAA %>%
  mutate(sd = ifelse(row_number()== 6 | row_number()== 7 | row_number()== 8, 12.4844389, sd))

coef_NAA <- coef_NAA %>%
 mutate(e_size = (estimate * sd)/0.4558857)

coef_NAA <- coef_NAA %>%
  rename(isd = sd)
```

```{r}
coef_NAA
```

> Effect size interpretation: small = 0.1, medium = 0.3, large = 0.5

> There are differences between age groups in intensity but not in rate of change dependent on DaysMax


