---
title: "200824 Merging imputed data"
author: "Anne Margit"
date: "8/24/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo= T, results='hide', message=F}
library(dplyr)
library(knitr)
library(tidyverse)
library(ggplot2)
library(psych)
```

```{r, echo= T, results='hide', message=F}
load("data_long_min3_str_age.Rdata")
load("selectieImputed2.Rdata")
```

Rename imputed variables: 
```{r, echo= T, results='hide', message=F}
selectieNew <- selectieImputed2 %>%
  rename("Ang_imp" = "Ang",
         "Anxiety_imp" = "Anxiety",
         "Calm_imp" = "Calm",
         "Depr_imp" = "Depr",
         "Energ_imp" = "Energ",
         "Exh_imp" = "Exh",
         "Insp_imp" = "Insp",
         "Nerv_imp" = "Nerv",
         "Rel_imp" = "Rel") 
```

Merge imputed dataset with original dataset:
```{r, echo= T, results='hide', message=F}
data_long_min3_str_age$ID <- as.factor(data_long_min3_str_age$ID)
selectieNew$ID <- as.factor(selectieNew$ID)

data_merge1 <- left_join(data_long_min3_str_age, selectieNew, by=c("ID", "Time"))
```

Create new variables in which rows that have no observations at all are coded missing:
These lines say: "If there is a missing on anger & anxiety & ... & relaxed, then revalue the emotion score to NA. Otherwise revalue to the imputed emotion score."  
```{r, echo= T, results='hide', message=F}
data_merge1$Ang_imp2 <- ifelse(is.na(data_merge1$Ang) & is.na(data_merge1$Anxiety) & is.na(data_merge1$Calm) & is.na(data_merge1$Depr) & is.na(data_merge1$Energ) & is.na(data_merge1$Exh) & is.na(data_merge1$Insp) & is.na(data_merge1$Nerv) & is.na(data_merge1$Rel), NA, data_merge1$Ang_imp)

data_merge1$Anxiety_imp2 <- ifelse(is.na(data_merge1$Ang) & is.na(data_merge1$Anxiety) & is.na(data_merge1$Calm) & is.na(data_merge1$Depr) & is.na(data_merge1$Energ) & is.na(data_merge1$Exh) & is.na(data_merge1$Insp) & is.na(data_merge1$Nerv) & is.na(data_merge1$Rel), NA, data_merge1$Anxiety_imp)

data_merge1$Calm_imp2 <- ifelse(is.na(data_merge1$Ang) & is.na(data_merge1$Anxiety) & is.na(data_merge1$Calm) &  is.na(data_merge1$Depr) & is.na(data_merge1$Energ) & is.na(data_merge1$Exh) & is.na(data_merge1$Insp) & is.na(data_merge1$Nerv) & is.na(data_merge1$Rel), NA, data_merge1$Calm_imp)

data_merge1$Depr_imp2 <- ifelse(is.na(data_merge1$Ang) & is.na(data_merge1$Anxiety) & is.na(data_merge1$Calm) &  is.na(data_merge1$Depr) & is.na(data_merge1$Energ) & is.na(data_merge1$Exh) & is.na(data_merge1$Insp) & is.na(data_merge1$Nerv) & is.na(data_merge1$Rel), NA, data_merge1$Depr_imp)

data_merge1$Energ_imp2 <- ifelse(is.na(data_merge1$Ang) & is.na(data_merge1$Anxiety) & is.na(data_merge1$Calm) &  is.na(data_merge1$Depr) & is.na(data_merge1$Energ) & is.na(data_merge1$Exh) & is.na(data_merge1$Insp) & is.na(data_merge1$Nerv) & is.na(data_merge1$Rel), NA, data_merge1$Energ_imp)

data_merge1$Exh_imp2 <- ifelse(is.na(data_merge1$Ang) & is.na(data_merge1$Anxiety) & is.na(data_merge1$Calm) &  is.na(data_merge1$Depr) & is.na(data_merge1$Energ) & is.na(data_merge1$Exh) & is.na(data_merge1$Insp) & is.na(data_merge1$Nerv) & is.na(data_merge1$Rel), NA, data_merge1$Exh_imp)

data_merge1$Insp_imp2 <- ifelse(is.na(data_merge1$Ang) & is.na(data_merge1$Anxiety) & is.na(data_merge1$Calm) &  is.na(data_merge1$Depr) & is.na(data_merge1$Energ) & is.na(data_merge1$Exh) & is.na(data_merge1$Insp) & is.na(data_merge1$Nerv) & is.na(data_merge1$Rel), NA, data_merge1$Insp_imp)

data_merge1$Nerv_imp2 <- ifelse(is.na(data_merge1$Ang) & is.na(data_merge1$Anxiety) & is.na(data_merge1$Calm) &  is.na(data_merge1$Depr) & is.na(data_merge1$Energ) & is.na(data_merge1$Exh) & is.na(data_merge1$Insp) & is.na(data_merge1$Nerv) & is.na(data_merge1$Rel), NA, data_merge1$Nerv_imp)

data_merge1$Rel_imp2 <- ifelse(is.na(data_merge1$Ang) & is.na(data_merge1$Anxiety) & is.na(data_merge1$Calm) &  is.na(data_merge1$Depr) & is.na(data_merge1$Energ) & is.na(data_merge1$Exh) & is.na(data_merge1$Insp) & is.na(data_merge1$Nerv) & is.na(data_merge1$Rel), NA, data_merge1$Rel_imp)
  
```

Drop other emotion variables (original items and imputed items)
```{r, echo= T, results='hide', message=F}
data_merge2 <- data_merge1 %>%
  select(-c("Ang", "Anxiety", "Calm", "Depr", "Energ", "Exh", "Insp", "Nerv", "Rel",
            "Ang_imp", "Anxiety_imp", "Calm_imp", "Depr_imp", "Energ_imp", "Exh_imp", "Insp_imp", "Nerv_imp", "Rel_imp"))
```

Rename variables:
```{r, echo= T, results='hide', message=F}
data_imputed <- data_merge2 %>%
  rename("Ang" = "Ang_imp2",
         "Anxiety" = "Anxiety_imp2",
         "Calm" = "Calm_imp2",
         "Depr" = "Depr_imp2",
         "Energ" = "Energ_imp2",
         "Exh" = "Exh_imp2",
         "Insp" = "Insp_imp2",
         "Nerv" = "Nerv_imp2",
         "Rel" = "Rel_imp2") 
```

Check original data
```{r, echo= T, message=F, warning=F}
summary(data_long_min3_str_age[,7:15])
```
Compare original data and imputed data
```{r, echo= T, message=F, warning=F}
summary(data_imputed[,20:28])
```

Nu hebben alle emoties evenveel missings. Is dit logisch? 


Maak wat plotjes met lijnen per id, op een selectie van de eerste 15 personen:
```{r, echo= T, warning=F}
class(data_long_min3_str_age$ID)
data_long_min3_str_age$ID2 <- as.numeric(data_long_min3_str_age$ID)
describe(data_long_min3_str_age$ID2)
```

```{r, echo=T, warning=F}
class(data_imputed$ID)
data_imputed$ID2 <- as.numeric(data_imputed$ID)
describe(data_imputed$ID2)
```

Originele data:
```{r, echo= T, message=F, warning=F}
plot1<- ggplot(data = data_long_min3_str_age[which(data_long_min3_str_age$ID2 <16), ], aes(x = Time, y = Ang, color=as.factor(ID2))) + geom_line() + geom_point() + facet_wrap(. ~ ID2, nrow=3)

plot1
```

Originele data gemerged met geimputeerde data:
```{r, echo= T, message=F, warning=F}
plot2<- ggplot(data = data_imputed[which(data_imputed$ID2 <16), ], aes(x = Time, y = Ang, color=as.factor(ID2))) + geom_line() + geom_point() + facet_wrap(. ~ ID2, nrow=3)

plot2
```

```{r, echo= T, results='hide'}
save(data_imputed, file="data_imputed.Rdata")
```


