---
title: "First analyses three level"
author: "Anne Margit"
date: "8/27/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, set-options, echo=FALSE, cache= FALSE}
options(width=1000)
```

```{r, results = "hide"}
load("data_imputed_emomeans_maxweeks.Rdata")
```

This dataset includes:

1. Data from all weekly measurement waves (baseline through wave 11, Time 1 through 12) 
2. Participants who provided at least 3 measurements 
3. Participants who are residents of the country they currently live in
4. Participants who provided info on age
5. Participants who provided info on gender (either male or female)
6. Data from countries with at least 20 participants
7. Pooled age groups
8. Imputed missing emotion scores
9. Combined emotion scores (NAA, NAD, PAA, PAD)
10. An imputed Stringency index (StringencyIndex_imp) 
11. A variable indicating the number of days before and after the day on which maximum stringency was reached for the respective country (DaysMax)
12. A variable indicating the number of weeks before and after the day on which maximum stringency was reached for the respective country (WeeksMax)
13. A variable indicating the date on which maximum Stringency was reached for that country (DateMaxStr)

```{r, message=F}
library(dplyr)
library(tidyverse)
library(papaja)
library(ggpubr)
library(ggplot2)
library(lme4)
library(lmerTest)
library(rockchalk)
library(effects)
```

# Preparation

**Dummy coding Stringency**
*During the peak = 0 (all days with maximum stringency). Before peak = 1, after peak = 2*
```{r, results='hide', message=F}
data_analyse1 <- data_imputed_emomeans_maxweeks %>%
  group_by(Country) %>%
  mutate(Str_dummy = ifelse(Date < DateMaxStr, 1, ifelse(Date == DateMaxStr, 0, 2)))

data_analyse1$Str_dummy <- as_factor(data_analyse1$Str_dummy)
```

# Regression models

**Negative affect high arousal**

*Random intercept*
```{r, message=F, comment=NA}
model_NAA0 <- lmer(NAA ~ 1 + (1 | Country/ID), data = data_analyse1)
summary(model_NAA0)
```

*Stringency Index*
```{r, message=F, comment=NA}
model_NAA1 <- lmer(NAA ~ 1 + StringencyIndex + (1 | Country/ID), data = data_analyse1)
summary(model_NAA1)
anova(model_NAA0, model_NAA1)
```

*Stringency Index and dummy variable with 0 = days during maximum stringency, 1 = before, 2 = after*
```{r, message=F, comment=NA}
model_NAA2 <- lmer(NAA ~ 1 + StringencyIndex + Str_dummy + (1 | Country/ID), data = data_analyse1)
summary(model_NAA2)
anova(model_NAA1, model_NAA2)
```

*Stringency Index x dummy interaction*
```{r, message=F, comment=NA}
model_NAA3 <- lmer(NAA ~ 1 + StringencyIndex + Str_dummy +  StringencyIndex*Str_dummy + (1 | Country/ID), data = data_analyse1)
summary(model_NAA3)
anova(model_NAA2, model_NAA3)
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_NAA <- effect("StringencyIndex:Str_dummy", model_NAA3)

plot_NAA <- ggplot(as.data.frame(ef_NAA), 
       aes(StringencyIndex, fit, color=Str_dummy)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_bw(base_size=12) + scale_color_discrete(name="Maximum stringency", labels = c("During the peak", "Before the peak", "After the peak"))
```

```{r, message=F}
plot_NAA
```

**Negative affect low arousal**

*Random intercept*
```{r, message=F, comment=NA}
model_NAD0 <- lmer(NAD ~ 1 + (1 | Country/ID), data = data_analyse1)
summary(model_NAD0)
```

*Stringency Index*
```{r, message=F, comment=NA}
model_NAD1 <- lmer(NAD ~ 1 + StringencyIndex + (1 | Country/ID), data = data_analyse1)
summary(model_NAD1)
anova(model_NAD0, model_NAD1)
```

*Stringency Index and dummy variable with 0 = before maximum stringency, 1 = at or after*
```{r, message=F, comment=NA}
model_NAD2 <- lmer(NAD ~ 1 + StringencyIndex + Str_dummy + (1 | Country/ID), data = data_analyse1)
summary(model_NAD2)
anova(model_NAD1, model_NAD2)
```

*Stringency Index x dummy interaction*
```{r, message=F, comment=NA}
model_NAD3 <- lmer(NAD ~ 1 + StringencyIndex + Str_dummy +  StringencyIndex*Str_dummy + (1 | Country/ID), data = data_analyse1)
summary(model_NAD3)
anova(model_NAD2, model_NAD3)
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_NAD <- effect("StringencyIndex:Str_dummy", model_NAD3)

plot_NAD <- ggplot(as.data.frame(ef_NAD), 
       aes(StringencyIndex, fit, color=Str_dummy)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_bw(base_size=12) + scale_color_discrete(name="Maximum stringency", labels = c("During the peak", "Before the peak", "After the peak"))
```

```{r, message=F}
plot_NAD
```

**Positive affect high arousal**

*Random intercept*
```{r, message=F, comment=NA}
model_PAA0 <- lmer(PAA ~ 1 + (1 | Country/ID), data = data_analyse1)
summary(model_PAA0)
```

*Stringency Index*
```{r, message=F, comment=NA}
model_PAA1 <- lmer(PAA ~ 1 + StringencyIndex + (1 | Country/ID), data = data_analyse1)
summary(model_PAA1)
anova(model_PAA0, model_PAA1)
```

*Stringency Index and dummy variable with 0 = before maximum stringency, 1 = at or after*
```{r, message=F, comment=NA}
model_PAA2 <- lmer(PAA ~ 1 + StringencyIndex + Str_dummy + (1 | Country/ID), data = data_analyse1)
summary(model_PAA2)
anova(model_PAA1, model_PAA2)
```

*Stringency Index x dummy interaction*
```{r, message=F, comment=NA}
model_PAA3 <- lmer(PAA ~ 1 + StringencyIndex + Str_dummy +  StringencyIndex*Str_dummy + (1 | Country/ID), data = data_analyse1)
summary(model_PAA3)
anova(model_PAA2, model_PAA3)
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_PAA <- effect("StringencyIndex:Str_dummy", model_PAA3)

plot_PAA <- ggplot(as.data.frame(ef_PAA), 
       aes(StringencyIndex, fit, color=Str_dummy)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_bw(base_size=12) + scale_color_discrete(name="Maximum stringency", labels = c("During the peak", "Before the peak", "After the peak"))
```

```{r, message=F}
plot_PAA
```

**Positive affect low arousal**

*Random intercept*
```{r, message=F, comment=NA}
model_PAD0 <- lmer(PAD ~ 1 + (1 | Country/ID), data = data_analyse1)
summary(model_PAD0)
```

*Stringency Index*
```{r, message=F, comment=NA}
model_PAD1 <- lmer(PAD ~ 1 + StringencyIndex + (1 | Country/ID), data = data_analyse1)
summary(model_PAD1)
anova(model_PAD0, model_PAD1)
```

*Stringency Index and dummy variable with 0 = before maximum stringency, 1 = at or after*
```{r, message=F, comment=NA}
model_PAD2 <- lmer(PAD ~ 1 + StringencyIndex + Str_dummy + (1 | Country/ID), data = data_analyse1)
summary(model_PAD2)
anova(model_PAD1, model_PAD2)
```

*Stringency Index x dummy interaction*
```{r, message=F, comment=NA}
model_PAD3 <- lmer(PAD ~ 1 + StringencyIndex + Str_dummy +  StringencyIndex*Str_dummy + (1 | Country/ID), data = data_analyse1)
summary(model_PAD3)
anova(model_PAD2, model_PAD3)
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_PAD <- effect("StringencyIndex:Str_dummy", model_PAD3)

plot_PAD <- ggplot(as.data.frame(ef_PAD), 
       aes(StringencyIndex, fit, color=Str_dummy)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_bw(base_size=12) + scale_color_discrete(name="Maximum stringency", labels = c("During the peak", "Before the peak", "After the peak"))
```

```{r, message=F}
plot_PAD
```




