---
title: "First analyses different dummy coding"
author: "Anne Margit"
date: "9/02/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, set-options, echo=FALSE, cache= FALSE}
options(width=1000)
```

```{r, results = "hide"}
load("data_imputed_emomeans_maxweeks.Rdata")
```

This dataset includes:

1. Data from all weekly measurement waves (baseline through wave 11, Time 1 through 12) 
2. Participants who provided at least 3 measurements 
3. Participants who are residents of the country they currently live in
4. Participants who provided info on age
5. Participants who provided info on gender (either male or female)
6. Data from countries with at least 20 participants
7. Pooled age groups
8. Imputed missing emotion scores
9. Combined emotion scores (NAA, NAD, PAA, PAD)
10. An imputed Stringency index (StringencyIndex_imp) 
11. A variable indicating the number of days before and after the day on which maximum stringency was reached for the respective country (DaysMax)
12. A variable indicating the number of weeks before and after the day on which maximum stringency was reached for the respective country (WeeksMax)
13. A variable indicating the date on which maximum Stringency was reached for that country (DateMaxStr)

> My comments are in block quotes such as this. 

```{r, message=F}
library(dplyr)
library(tidyverse)
library(papaja)
library(ggpubr)
library(ggplot2)
library(lme4)
library(lmerTest)
library(rockchalk)
library(effects)
```

# Preparation

**Dummy coding Stringency**
*Before the peak = 0. During peak = 1 (all days with maximum stringency), after peak = 2*
```{r, results='hide', message=F}
data_analyse1 <- data_imputed_emomeans_maxweeks %>%
  group_by(Country) %>%
  mutate(Str_dummy = ifelse(Date < DateMaxStr, 0, ifelse(Date == DateMaxStr, 1, 2)))

data_analyse1$Str_dummy <- as_factor(data_analyse1$Str_dummy)

Dummy_N <- data_analyse1 %>%
group_by(Str_dummy) %>%
  summarise(N_dummy = n())
```

```{r, message=F}
apa_table(Dummy_N)
```

# Regression models

**Negative affect high arousal**

*Random intercept*
```{r, message=F, comment=NA}
model_NAA0 <- lmer(NAA ~ 1 + (1 | Country/ID), data = data_analyse1)
summary(model_NAA0)
```

*Stringency Index*
```{r, message=F, comment=NA}
model_NAA1 <- lmer(NAA ~ 1 + StringencyIndex + (1 | Country/ID), data = data_analyse1)
summary(model_NAA1)
anova(model_NAA0, model_NAA1)
```

> Overall positive relationship between stringency and NAA

*Stringency Index and dummy variable with 0 = days before maximum stringency, 1 = during, 2 = after*
```{r, message=F, comment=NA}
model_NAA2 <- lmer(NAA ~ 1 + StringencyIndex + Str_dummy + (1 | Country/ID), data = data_analyse1)
summary(model_NAA2)
anova(model_NAA1, model_NAA2)
```

> Lower NAA during the peak and after the peak compared to before the peak.

*Stringency Index x dummy interaction*
```{r, message=F, comment=NA}
model_NAA3 <- lmer(NAA ~ 1 + StringencyIndex + Str_dummy +  StringencyIndex*Str_dummy + (1 | Country/ID), data = data_analyse1)
summary(model_NAA3)
anova(model_NAA2, model_NAA3)
```

> Compared to before the peak, association between stringency and NAA is more positive during and after the peak. This model has better fit than previous one without the interaction. 

*Random slope for Stringency Index on level 3*
```{r, message=F, comment=NA}
model_NAA4 <- lmer(NAA ~ 1 + StringencyIndex + Str_dummy +  StringencyIndex*Str_dummy + (1 | Country/ID)
                   + (StringencyIndex | Country), data = data_analyse1)
summary(model_NAA4)
anova(model_NAA3, model_NAA4)
```

> Model including a random slope for stringency index is a better fit than previous model. 

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_NAA <- effect("StringencyIndex:Str_dummy", model_NAA3)

plot_NAA <- ggplot(as.data.frame(ef_NAA), 
       aes(StringencyIndex, fit, color=Str_dummy)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_bw(base_size=12) + scale_color_discrete(name="Maximum stringency", labels = c("Before the peak", "During the peak", "After the peak"))
```

```{r, message=F}
plot_NAA
```

**Negative affect low arousal**

*Random intercept*
```{r, message=F, comment=NA}
model_NAD0 <- lmer(NAD ~ 1 + (1 | Country/ID), data = data_analyse1)
summary(model_NAD0)
```

*Stringency Index*
```{r, message=F, comment=NA}
model_NAD1 <- lmer(NAD ~ 1 + StringencyIndex + (1 | Country/ID), data = data_analyse1)
summary(model_NAD1)
anova(model_NAD0, model_NAD1)
```

> Overall positive relationship between stringency and NAD

*Stringency Index and dummy variable with 0 = before maximum stringency, 1 = during peak, 2 = after*
```{r, message=F, comment=NA}
model_NAD2 <- lmer(NAD ~ 1 + StringencyIndex + Str_dummy + (1 | Country/ID), data = data_analyse1)
summary(model_NAD2)
anova(model_NAD1, model_NAD2)
```

> NAD is higher during stringency peak compared to before peak, no difference in NAD after the peak compared to before the peak. Model including dummy variables is not a better fit, previous model is best. 

*Stringency Index x dummy interaction*
```{r, message=F, comment=NA}
model_NAD3 <- lmer(NAD ~ 1 + StringencyIndex + Str_dummy +  StringencyIndex*Str_dummy + (1 | Country/ID), data = data_analyse1)
summary(model_NAD3)
anova(model_NAD2, model_NAD3)
```

> No significant interaction effect

*Random slope for stringency index without dummy variable and interaction*
```{r, message=F, comment=NA}
model_NAD4 <- lmer(NAD ~ 1 + StringencyIndex + (1  | Country/ID) + (StringencyIndex | Country), data = data_analyse1)
summary(model_NAD4)
anova(model_NAD1, model_NAD4)
```

> Model met random slope is beter dan met fixed slope, maar geeft wel een warning (failed to converge?)


*Plot of predicted values*
```{r, results = "hide", message=F}
ef_NAD <- effect("StringencyIndex:Str_dummy", model_NAD3)

plot_NAD <- ggplot(as.data.frame(ef_NAD), 
       aes(StringencyIndex, fit, color=Str_dummy)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_bw(base_size=12) + scale_color_discrete(name="Maximum stringency", labels = c("Before the peak", "During the peak", "After the peak"))
```

```{r, message=F}
plot_NAD
```

**Positive affect high arousal**

*Random intercept*
```{r, message=F, comment=NA}
model_PAA0 <- lmer(PAA ~ 1 + (1 | Country/ID), data = data_analyse1)
summary(model_PAA0)
```

*Stringency Index*
```{r, message=F, comment=NA}
model_PAA1 <- lmer(PAA ~ 1 + StringencyIndex + (1 | Country/ID), data = data_analyse1)
summary(model_PAA1)
anova(model_PAA0, model_PAA1)
```

> Overall negative relationship between stringency and PAA. Model with stringency index fits better than without predictors

*Stringency Index and dummy variable with 0 = before maximum stringency, 1 = during peak, 2 = after*
```{r, message=F, comment=NA}
model_PAA2 <- lmer(PAA ~ 1 + StringencyIndex + Str_dummy + (1 | Country/ID), data = data_analyse1)
summary(model_PAA2)
anova(model_PAA1, model_PAA2)
```

> PAA is higher after the peak compared to before the peak. No difference in PAA before the peak compared to during the peak. This model fits better than model with only stringency index as predictor.

*Stringency Index x dummy interaction*
```{r, message=F, comment=NA}
model_PAA3 <- lmer(PAA ~ 1 + StringencyIndex + Str_dummy +  StringencyIndex*Str_dummy + (1 | Country/ID), data = data_analyse1)
summary(model_PAA3)
anova(model_PAA2, model_PAA3)
```

> Both interactions are significant: compared to before the peak, the relationship between stringency and PAA is more negative during and after the peak. Model with interaction effects is a better fit. 

*Random slope for Stringency Index*
```{r, message=F, comment=NA}
model_PAA4 <- lmer(PAA ~ 1 + StringencyIndex + Str_dummy +  StringencyIndex*Str_dummy + (1  | Country/ID) 
                   + (1 + StringencyIndex | Country), data = data_analyse1)
summary(model_PAA4)
anova(model_PAA3, model_PAA4)
```

> Random slope is significant

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_PAA <- effect("StringencyIndex:Str_dummy", model_PAA3)

plot_PAA <- ggplot(as.data.frame(ef_PAA), 
       aes(StringencyIndex, fit, color=Str_dummy)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_bw(base_size=12) + scale_color_discrete(name="Maximum stringency", labels = c("Before the peak", "During the peak", "After the peak"))
```

```{r, message=F}
plot_PAA
```

**Positive affect low arousal**

*Random intercept*
```{r, message=F, comment=NA}
model_PAD0 <- lmer(PAD ~ 1 + (1 | Country/ID), data = data_analyse1)
summary(model_PAD0)
```

*Stringency Index*
```{r, message=F, comment=NA}
model_PAD1 <- lmer(PAD ~ 1 + StringencyIndex + (1 | Country/ID), data = data_analyse1)
summary(model_PAD1)
anova(model_PAD0, model_PAD1)
```

> Overall negative association between stringency and PAD

*Stringency Index and dummy variable with 0 = before maximum stringency, 1 = during, 2 = after*
```{r, message=F, comment=NA}
model_PAD2 <- lmer(PAD ~ 1 + StringencyIndex + Str_dummy + (1 | Country/ID), data = data_analyse1)
summary(model_PAD2)
anova(model_PAD1, model_PAD2)
```

> PAD is higher after maximum stringency compared to before.

*Stringency Index x dummy interaction*
```{r, message=F, comment=NA}
model_PAD3 <- lmer(PAD ~ 1 + StringencyIndex + Str_dummy +  StringencyIndex*Str_dummy + (1 | Country/ID), data = data_analyse1)
summary(model_PAD3)
anova(model_PAD2, model_PAD3)
```

> Both interaction effects are significant: compared to before the peak, association between stringency and PAD is more negative during and after the peak.

*Random slope voor stringency*
```{r, message=F, comment=NA}
model_PAD4 <- lmer(PAD ~ 1 + StringencyIndex + Str_dummy +  StringencyIndex*Str_dummy + (1 | Country/ID)
                   + (1 + StringencyIndex | Country), data = data_analyse1)
summary(model_PAD4)
anova(model_PAD3, model_PAD4)
```

> Better fit with random slope

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_PAD <- effect("StringencyIndex:Str_dummy", model_PAD3)

plot_PAD <- ggplot(as.data.frame(ef_PAD), 
       aes(StringencyIndex, fit, color=Str_dummy)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_bw(base_size=12) + scale_color_discrete(name="Maximum stringency", labels = c("Before the peak", "During the peak", "After the peak"))
```

```{r, message=F}
plot_PAD
```




