---
title: "First analyses three-level centered"
author: "Anne Margit"
date: "9/08/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, set-options, echo=FALSE, cache= FALSE}
options(width=1000)
```

```{r, results = "hide"}
load("data_imputed_emomeans_maxmin.Rdata")
```

This dataset includes:

1. Data from all weekly measurement waves (baseline through wave 11, Time 1 through 12) 
2. Participants who provided at least 3 measurements 
3. Participants who are residents of the country they currently live in
4. Participants who provided info on age
5. Participants who provided info on gender (either male or female)
6. Data from countries with at least 20 participants
7. Pooled age groups
8. Imputed missing emotion scores
9. Combined emotion scores (NAA, NAD, PAA, PAD)
10. An imputed Stringency index (StringencyIndex_imp) 
11. A variable indicating the number of days before and after the day on which maximum stringency was reached for the respective country (DaysMax)
12. A variable indicating the number of weeks before and after the day on which maximum stringency was reached for the respective country (WeeksMax)
13. A variable indicating the date on which maximum Stringency was reached for that country (DateMaxStr)

> My comments are in block quotes such as this. 

```{r, message=F}
library(dplyr)
library(tidyverse)
library(papaja)
library(ggpubr)
library(ggplot2)
library(lme4)
library(lmerTest)
library(rockchalk)
library(effects)
library(nlme)
library(lattice)
```

# Preparation

**Dummy coding Stringency**
*Before the peak = 0. During peak = 1 (all days with maximum stringency), after peak = 2*
```{r, results='hide', message=F}
data_analyse1 <- data_imputed_emomeans_maxmin %>%
  group_by(Country) %>%
  mutate(Str_dummy = ifelse(Date < DateMaxStr, 0, ifelse(StringencyIndex == MaxStr & Date >= DateMaxStr, 1, 2)))

data_analyse1$Str_dummy <- as_factor(data_analyse1$Str_dummy)

Dummy_N <- data_analyse1 %>%
group_by(Str_dummy) %>%
  summarise(N_dummy = n())
```

```{r, message=F}
apa_table(Dummy_N)
```

```{r, message=F}
g_dummy1 <- data_analyse1 %>%
filter(Country == "Netherlands") %>%
  filter(!is.na(Date)) %>%
  ggplot(aes(x=Date, y=Str_dummy))

g_dummy1 + geom_line() 
```
```{r, message=F}
g_dummy2 <- data_analyse1 %>%
filter(Country == "Indonesia") %>%
  filter(!is.na(Date)) %>%
  ggplot(aes(x=Date, y=Str_dummy))

g_dummy2 + geom_line() 
```


# Filter countries with a second peak
A few countries have a second peak in stringency.
These are:

1. Germany, starting at 2020-06-19
2. Greece, starting at 2020-06-22
3. Italy: starting at 2020-06-11
4. Philippines: starting at 2020-06-15
5. South Korea: starting at 2020-05-30
6. United Kingdom: starting at 2020-06-08

```{r, message=F, comment=NA}
data_analyse1 <- data_analyse1[with(data_analyse1, order(Country, Date)),]

data_analyse1_f <- data_analyse1[!(data_analyse1$Country == "Germany" & data_analyse1$Date >= "2020-06-19"),]
tail(data_analyse1_f[which(data_analyse1_f$Country == "Germany"),]$Date, n=10L)

data_analyse1_f <- data_analyse1_f[!(data_analyse1_f$Country == "Greece" & data_analyse1_f$Date >= "2020-06-22"),]
tail(data_analyse1_f[which(data_analyse1_f$Country == "Greece"),]$Date, n=10L)

data_analyse1_f <- data_analyse1_f[!(data_analyse1_f$Country == "Italy" & data_analyse1_f$Date >= "2020-06-11"),]
tail(data_analyse1_f[which(data_analyse1_f$Country == "Italy"),]$Date, n=10L)

data_analyse1_f <- data_analyse1_f[!(data_analyse1_f$Country == "Philippines" & data_analyse1_f$Date >= "2020-06-15"),]
tail(data_analyse1_f[which(data_analyse1_f$Country == "Philippines"),]$Date, n=10L)

data_analyse1_f <- data_analyse1_f[!(data_analyse1_f$Country == "South Korea" & data_analyse1_f$Date >= "2020-05-30"),]
tail(data_analyse1_f[which(data_analyse1_f$Country == "South Korea"),]$Date, n=10L)

data_analyse1_f <- data_analyse1_f[!(data_analyse1_f$Country == "United Kingdom" & data_analyse1_f$Date >= "2020-06-08"),]
tail(data_analyse1_f[which(data_analyse1_f$Country == "United Kingdom"),]$Date, n=10L)
```

>  This excludes 583 observations from the analyses

```{r, message=F, comment=NA}
save(data_analyse1_f, file="data_analyse1_f.Rdata")
```

# Country mean centering Stringency Index
```{r, results = "hide", message=F}
data_analyse1_fc <- gmc(data_analyse1_f, "StringencyIndex", "Country", FUN = mean, suffix = c("_mn", "_dev"),
    fulldataframe = TRUE)
```
# Regression models

> Using nlme instead of lme4 because it allows for more complex variance covariance structures. Lme4 has as default unstructured. Default = ML 

**Negative affect high arousal**

*Stringency Index x dummy interaction*
```{r, message=F, comment=NA}
model_NAA <- lme(fixed = NAA ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                  random = ~1 | Country/ID, 
                 data = data_analyse1_fc, 
                 na.action = na.omit)

summary(model_NAA)
```

*Random slope for Stringency Index at level 3 (Country)*
```{r, message=F, comment=NA}
model_NAA2 <- lme(fixed = NAA ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                  random = list (Country = ~StringencyIndex_dev, ID = ~1), 
                  data = data_analyse1_fc, 
                  na.action = na.omit)

summary(model_NAA2)
anova(model_NAA, model_NAA2)
```
*Random slope for Stringency Index at level 2 and 3*
```{r, message=F, comment=NA}
model_NAA3 <- lme(fixed = NAA ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                  random = ~StringencyIndex_dev | Country/ID, 
                  data = data_analyse1_fc, 
                  na.action = na.omit)

summary(model_NAA3)
anova(model_NAA2, model_NAA3)
```

> Model with random slopes at both levels has better fit.

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_NAA3)
```

*Plot random intercepts and slopes*
```{r, message=F, comment=NA}
plot(ranef(model_NAA3, level = 1))
```

> Intercepts appear normally distributed except for the Netherlands and Germany, slightly negative. Slopes are randomly distributed as well, but United States slightly negative? 

*QQ plots to compare residual distributions*
```{r, message=F, comment=NA}
par(mfrow = c(1,2))
lims <- c(-3.5,3.5)
qqnorm(resid(model_NAA2, type = "normalized"),
xlim = lims, ylim = lims,main = "Random slope at Country level")
abline(0,1, col = "red", lty = 2)
qqnorm(resid(model_NAA3, type = "normalized"),
xlim = lims, ylim = lims, main = "Random slope at Country and ID")
abline(0,1, col = "red", lty = 2)
```

> Residual distributions do not change much between models

*QQ plots to compare residual distributions between model with and without random slopes*
```{r, message=F, comment=NA}
par(mfrow = c(1,2))
lims <- c(-3.5,3.5)
qqnorm(resid(model_NAA, type = "normalized"),
xlim = lims, ylim = lims,main = "No random slopes")
abline(0,1, col = "red", lty = 2)
qqnorm(resid(model_NAA3, type = "normalized"),
xlim = lims, ylim = lims, main = "Random slope at Country and ID")
abline(0,1, col = "red", lty = 2)
```

> Not much improvement 

*Random slope for Str_dummy op country level (and Stringency)*
```{r, eval = FALSE}
model_NAA4 <- lme(fixed = NAA ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                  random = list (Country = ~ StringencyIndex_dev + Str_dummy, ID = ~ StringencyIndex_dev), 
                  data = data_analyse1_fc, 
                  na.action = na.omit)

summary(model_NAA4)
```

> Failed to converge 

*Changing model iteration limit and model optimizer*
```{r, message=F, comment=NA}
model_NAA4 <- lme(fixed = NAA ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                  random = list (Country = ~ StringencyIndex_dev + Str_dummy, ID = ~ StringencyIndex_dev), 
                  data = data_analyse1_fc, 
                  na.action = na.omit,
                  control = list(maxIter = 100, opt = "optim"))

summary(model_NAA4)
anova(model_NAA3, model_NAA4)
```

> Including random slope for Str_dummy on level 3 improves model fit

*Plot random intercepts and slopes*
```{r, message=F, comment=NA}
plot(ranef(model_NAA4, level = 1))
```

*QQ plots to compare residual distributions*
```{r, message=F, comment=NA}
par(mfrow = c(1,2))
lims <- c(-3.5,3.5)
qqnorm(resid(model_NAA3, type = "normalized"),
xlim = lims, ylim = lims,main = "Model NAA3")
abline(0,1, col = "red", lty = 2)
qqnorm(resid(model_NAA4, type = "normalized"),
xlim = lims, ylim = lims, main = "Model NAA4")
abline(0,1, col = "red", lty = 2)
```

> NAA3 = random slopes for stringency on level 2 and 3, NAA4 = NAA3 + random slope Str_Dummy level 3 

*Random slopes for Str_dummy on level 2 and 3*
```{r, eval = FALSE}
model_NAA5 <- lme(fixed = NAA ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                  random = ~ StringencyIndex_dev + Str_dummy | Country/ID,
                  data = data_analyse1_fc, 
                  na.action = na.omit,
                  control = list(maxIter = 100, opt = "optim"))

summary(model_NAA5)
anova(model_NAA3, model_NAA4)
```

> Kreeg een hele lang error 

*Autoregressive correlation structure*

> Using the corCAR1 error structure assumes that assessments are taken in varying intervals.  

```{r, eval = FALSE}
model_NAA6 <- lme(fixed = NAA ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                  random = list (Country = ~ StringencyIndex_dev + Str_dummy, ID = ~ StringencyIndex_dev),
                  data = data_analyse1_fc, 
                  na.action = na.omit,
                  correlation = corCAR1(),
                  control = list(maxIter = 100, opt = "optim"))

summary(model_NAA6)
anova(model_NAA3, model_NAA4)
```

> Ook een error (NA in foreign function call??)

*Plot of predicted values: random slope model for Str_dummy op level 3 and stringency on level 2 and 3*
```{r, results = "hide", message=F}
ef_NAA <- effect("StringencyIndex_dev:Str_dummy", model_NAA4)

plot_NAA <- ggplot(as.data.frame(ef_NAA), 
       aes(StringencyIndex_dev, fit, color=Str_dummy)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_bw(base_size=12) + scale_color_discrete(name="Maximum stringency", labels = c("Before the peak", "During the peak", "After the peak"))
```

```{r, message=F}
plot_NAA
```





