---
title: "NAD all phases winning models and quadratic and new colors"
author: "Anne Margit"
date: "03/05/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, set-options, echo=FALSE, cache= FALSE}
options(width=1000)
Sys.getenv('R_MAX_VSIZE')
```

```{r, results = "hide"}
load("data_analyse2_p1.Rdata")
load("data_analyse2_p2.Rdata")
load("data_analyse2_p3.Rdata")
```

This dataset includes:

1. Data from all weekly measurement waves (baseline through wave 11, Time 1 through 12) 
2. Participants who provided at least 3 measurements 
3. Participants who are residents of the country they currently live in
4. Participants who provided info on age
5. Participants who provided info on gender (either male or female)
6. Data from countries with at least 20 participants
7. Pooled age groups
8. Imputed missing emotion scores
9. Combined emotion scores (NAA, NAD, PAA, PAD)
10. An imputed Stringency index (StringencyIndex_imp) 
11. A dummy Str_dummy with 0 = before the peak, 1 = during peak, 2 = after peak
12. A variable indicating the number of days before maximum stringency was reached (DaysMax_p1), during (DaysMax_p2), and after (DaysPhase3)
13.  A variable indicating the number of weeks before maximum stringency was reached (WeeksMax_p1), during (WeeksMax_p2), and after (WeeksPhase3)
14. A variable indicating the date on which maximum Stringency was reached for that country (DateMaxStr) and the max level reached (MaxStr) across the entire measurement period
15. A variable indicating the date on which minimum Stringency was reached for that country (DateMinStr) and the min level reached (MinStr) across the entire measurement period
15. Observations during which there was a second peak are excluded (N=583) 

> My comments are in block quotes such as this. 

```{r, message=F}
library(dplyr)
library(tidyverse)
library(ggpubr)
library(ggplot2)
library(rockchalk)
library(effects)
library(nlme)
library(lattice)
library(broom.mixed)
library(purrr)
library(stargazer)
library(viridis)
```

# Descriptives
**Number of participants per age group**

> 0 = 18-24, 1 = 25-44, 3= 45-64, 4= 65+

Phase 1
```{r, message=F, comment=NA}
data_analyse2_p1 %>%
  group_by(Age_new) %>%
  summarise(NAge = n())
```

Phase 2
```{r, message=F, comment=NA}
data_analyse2_p2 %>%
  group_by(Age_new) %>%
  summarise(NAge = n())
```

Phase 3
```{r, message=F, comment=NA}
data_analyse2_p2 %>%
  group_by(Age_new) %>%
  summarise(NAge = n())
```

**Plots**
**Mean NAD against max stringency in WEEKS**
Phase 1 (only age differences)
```{r, echo=T, message=F, warning=F}
plot_NAD1 <- ggplot(data_analyse2_p1, aes(x=Age_new, y=NAD, group = Age_new, color = Age_new))

plot_NAD1 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0.5) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

Phase 2
```{r, echo=T, message=F, warning=F}
plot_NAD2 <- ggplot(data_analyse2_p2, aes(x=WeeksMax_p2, y=NAD, group = Age_new, color = Age_new))

plot_NAD2 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

Phase 3
```{r, echo=T, message=F, warning=F}
plot_NAD3 <- ggplot(data_analyse2_p3, aes(x=WeeksPhase3, y=NAD, group = Age_new, color = Age_new))

plot_NAD3 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

**Mean NAD against max stringency in DAYS**
Phase 2
```{r, echo=T, message=F, warning=F}
plot_NAD2 <- ggplot(data_analyse2_p2, aes(x=DaysMax_p2, y=NAD, group = Age_new, color = Age_new))

plot_NAD2 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

Phase 3
```{r, echo=T, message=F, warning=F}
plot_NAD3 <- ggplot(data_analyse2_p3, aes(x=DaysPhase3, y=NAD, group = Age_new, color = Age_new))

plot_NAD3 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

# Phase 1
*Random: IC for ID and Country + Covariates Gender and Education*

> Gender: Male = 0, Female = 1

> Edu: 0= Primary education, 1= General secondary education, 2= Vocational education, 3= Higher education, 4= Bachelors degree, 5= Masters degree, 6= PhD degree

```{r, message=F, comment=NA}
data_analyse2_p1$Edu <- as.numeric(data_analyse2_p1$Edu)
model_NADp1 <- lme(fixed = NAD ~ Gender + Edu + Age_new,
                  random = ~1 | Country/ID, 
                  data = data_analyse2_p1, 
                  na.action = na.omit)

summary(model_NADp1)
VarCorr(model_NADp1)
```

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_NADp1)
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_NADp1 <- effect("Age_new", model_NADp1)

plot_NADp1 <- ggplot(as.data.frame(ef_NADp1), 
  aes(Age_new, fit, color=Age_new)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_minimal(base_size=12) + 
  labs(title="NAD before peak stringency", y = "NAD") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_discrete(name ="Age", labels=c("18-24", "25-44", "45-64", "65+")) +
  theme(legend.position = "none") +                 
  scale_color_discrete() + 
  expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_NADp1
```

*Effect sizes*
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p1 %>% 
  group_by(ID) %>%
  summarize_at(c("NAD"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("NAD"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect size = regression coefficient / average ISD of NAD

```{r, message=F, comment=NA}
coef_NADp1 = tidy(model_NADp1, 
               effects = "fixed")

coef_NADp1 <- coef_NADp1 %>%
  mutate (e_size = estimate/0.4838285) %>% 
  mutate(across(2:7, round, 2)) 
         
```

```{r}
coef_NADp1
coef_NADp1 <- as.matrix(coef_NADp1)
```

# Phase 2

*Best model*

> Random intercept for ID and Country, random slope for Country, AR correlation structure at Measuement level

```{r, message=F, comment=NA}
data_analyse2_p2$Edu <- as.numeric(data_analyse2_p2$Edu)
data_analyse2_p2 <- data_analyse2_p2[with(data_analyse2_p2, order(Country, ID, Time)),]
data_analyse2_p2$Time <- as.numeric(data_analyse2_p2$Time)

model_NADp2 <- lme(fixed = NAD ~ Gender + Edu + DaysMax_p2 + Age_new + DaysMax_p2*Age_new,
                  random = list (Country = ~1, ID = ~DaysMax_p2), 
                  data = data_analyse2_p2, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_NADp2)
VarCorr(model_NADp2)
```

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_NADp2, which = 'fixed')
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_NADp2 <- effect("DaysMax_p2:Age_new", model_NADp2)

plot_NADp2 <- ggplot(as.data.frame(ef_NADp2), aes(DaysMax_p2, fit, color=Age_new)) + 
  geom_line(size=1) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + 
  theme_minimal(base_size=12) + 
  labs(title="NAD trajectories during peak stringency",
       x="Days since start peak stringency", y = "NAD") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + 
  expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_NADp2
```

*Effect sizes*
**Within person SD and average within person SD**
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p2 %>% 
  group_by(ID) %>%
  summarize_at(c("DaysMax_p2", "NAD"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("DaysMax_p2", "NAD"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect sizes for intercept and main effect of age and covariates = regression coefficient / average ISD of NAD
> Effect size for main effect of DaysMax = (regression coefficient * 28)/ average ISD of NAD
> Effect sizes for interaction effects = (regression coefficient * 28)/ average ISD of NAD

> The effect sizes for main effect of DaysMax and the interaction effects reflect the increase in SD of NAD over 4 weeks (28 days)

```{r, message=F, comment=NA}
coef_NADp2 = tidy(model_NADp2, 
               effects = "fixed")

coef_NADp2 <- coef_NADp2 %>%
  mutate(e_size = ifelse(row_number()== 1 | row_number()== 2 |  row_number()== 3 |  row_number()== 5 |  row_number()== 6 |  row_number()== 7, estimate/0.4753929, (estimate*28)/0.4753929)) %>%
  mutate(across(2:7, round, 2)) 
          
```

```{r}
coef_NADp2
coef_NADp2 <- as.matrix(coef_NADp2)
```

> NAD decreases over time in the youngest age group (main effect), but not or minimally in the older age groups (interaction effect). Older people report lower NAD than the youngest age group at t=0 (first day of max stringency, main effect). 

```{r}
model_coefs <- coef(model_NADp2, level = 2)
  
model_coefs <- as.data.frame(model_coefs) %>%
rownames_to_column("ID")
  
model_coefs <- model_coefs %>%
separate(col = 1, into = c("Country", "ID"), sep = "\\/") %>%
dplyr::rename("Intercept" = "(Intercept)")
  
data2 <- left_join(data_analyse2_p2, model_coefs, by= "ID")
  
data3 <- data2 %>%
filter(Nmiss == 0) %>%
  filter(n > 5)
```

```{r}
labels <- c("0" = "Age 18-24", "1" = "Age 25-44", "2" = "Age 45-64", "3" = "Age 65+")

model_coef_plot <- ggplot(data = data3[which(data3$ID2 <200),], 
       mapping = aes(x = DaysMax_p2.x, y = NAD, colour = ID)) +
       geom_point() +
       geom_abline(aes(intercept = Intercept, 
                  slope = DaysMax_p2.y,
                  colour = ID),size = 0.5) + 
                  scale_x_continuous(limits = c(0, 100)) + 
                  theme(legend.position = "none") +
                  facet_wrap(~Age_new, 
                  labeller = labeller(Age_new = labels)) +
      xlab("Days since start peak stringency") +
      ggtitle("Predicted NAD trajectories for subsample of participants") +
      theme_minimal(base_size=12) + 
      scale_color_discrete() + 
      theme(plot.title = element_text(hjust = 0.5)) +
      theme(legend.position = "none") 

model_coef_plot

```  

# Random slope variation plot
```{r, message=F}
Age_labels <- c("18-24", "25-44", "45-64", "65+")
names(Age_labels) <- c("0","1","2","3")

plot_NADp2_slope <- ggplot(data2, aes(x= DaysMax_p2.y, fill = ..x..)) +
  geom_histogram() +
 scale_fill_viridis(option = "C")+
  theme_minimal()+
  theme(legend.position="none") + 
  labs(title="Variability in NAD trajectories during peak stringency",
       x="Regression coefficient (NAD ~ days)", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5)) +
   facet_wrap(~ Age_new, labeller = labeller(Age_new = Age_labels)) 

```

```{r}
plot_NADp2_slope 

```

# Quadratic term
The interaction between age and daysmax was significant so these are kept in the current model. The time variable needs to be centered at the midpoint (mean) to reduce collinearity between the linear and the quadratic components.

```{r, message=F, comment=NA}
data_analyse2_p2q <- gmc(data_analyse2_p2, "DaysMax_p2", "ID", FUN = mean, suffix = c("_mn", "_dev"),
    fulldataframe = TRUE)
```


```{r, message=F, comment=NA}
data_analyse2_p2q$Edu <- as.numeric(data_analyse2_p2q$Edu)

data_analyse2_p2q <- data_analyse2_p2q[with(data_analyse2_p2q, order(Country, ID, Time)),]
data_analyse2_p2q$Time <- as.numeric(data_analyse2_p2q$Time)

model_NADp2q <- lme(fixed = NAD ~ Gender + Edu + DaysMax_p2_dev + Age_new + DaysMax_p2_dev*Age_new +  
                    + I(DaysMax_p2_dev^2) + I(DaysMax_p2_dev^2)*Age_new,
                  random = list(Country = pdDiag(~ DaysMax_p2_dev), 
                  ID = ~DaysMax_p2_dev),
                  data = data_analyse2_p2q, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_NADp2q)
VarCorr(model_NADp2q)

```
Results suggest that there is a linear decline of NAD over time in the youngest age group. There was a significant decelerated decline in NAD over time in the age group 25-44 compared with the youngest age group. 

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_NADp2q, which = 'fixed')
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_NADp2q <- effect("Age_new:I(DaysMax_p2_dev^2)", model_NADp2q)

plot_NADp2q <- ggplot(as.data.frame(ef_NADp2q), aes(DaysMax_p2_dev, fit, color=Age_new)) + 
  geom_line(size=1) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + 
  theme_minimal(base_size=12) + 
  labs(title="Quadratic NAD trajectories during peak stringency",
       x="Days since start peak stringency (centered)", y = "NAD") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + 
  expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_NADp2q
```

# Phase 3

> Random IC for Country and ID, random S for ID, AR structure

```{r, message=F, comment=NA}
data_analyse2_p3$Edu <- as.numeric(data_analyse2_p3$Edu)
data_analyse2_p3 <- data_analyse2_p3[with(data_analyse2_p3, order(Country, ID, Time)),]
data_analyse2_p3$Time <- as.numeric(data_analyse2_p3$Time)

model_NADp3 <- lme(fixed = NAD ~ Gender + Edu + DaysPhase3 + Age_new + DaysPhase3*Age_new,
                  random = list (Country = ~1, ID = ~DaysPhase3), 
                  data = data_analyse2_p3, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_NADp3)
VarCorr(model_NADp3)
```

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_NADp3, which = 'fixed')
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_NADp3 <- effect("DaysPhase3:Age_new", model_NADp3)

plot_NADp3 <- ggplot(as.data.frame(ef_NADp3), aes(DaysPhase3, fit, color=Age_new)) + 
  geom_line(size=1) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + 
  theme_minimal(base_size=12) + 
  labs(title="NAD trajectories since decline in stringency",
       x="Days since decline in stringency", y = "NAD") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + 
  expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_NADp3
```
*Effect sizes*
**Within person SD and average within person SD for NAD**
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p3 %>% 
  group_by(ID) %>%
  summarize_at(c("NAD"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("NAD"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect sizes for intercept and main effect of age = regression coefficient / average ISD of NAD
> Effect size for main effect of DaysMax = (regression coefficient * 28)/ average ISD of NAD
> Effect sizes for interaction effects = (regression coefficient * 28)/ average ISD of NAD

> The effect sizes for main effect of DaysMax and the interaction effects reflect the increase in SD of NAD over 4 weeks (28 days)

```{r, message=F, comment=NA}
coef_NADp3 = tidy(model_NADp3, 
               effects = "fixed")

coef_NADp3 <- coef_NADp3 %>%
 mutate(e_size = ifelse(row_number()== 1 | row_number()== 2 |  row_number()== 3 |  row_number()== 5 |  row_number()== 6 |  row_number()== 7,  estimate/0.4574414, (estimate*28)/0.4574414)) %>%
  mutate(across(2:7, round, 2)) 
```

```{r}
coef_NADp3
coef_NADp3 <- as.matrix(coef_NADp3)
```

> NAD does not change over time in the youngest group (main effect) or older groups (interaction effect). All older age groups report lower NAD compared with the youngest on the first day when stringency reduces (main effect). 


```{r}
model_coefs <- coef(model_NADp3, level = 2)
  
model_coefs <- as.data.frame(model_coefs) %>%
rownames_to_column("ID")
  
model_coefs <- model_coefs %>%
separate(col = 1, into = c("Country", "ID"), sep = "\\/") %>%
dplyr::rename("Intercept" = "(Intercept)")
  
data2 <- left_join(data_analyse2_p3, model_coefs, by= "ID")
  
data3 <- data2 %>%
filter(Nmiss == 0) %>%
  filter(n > 5)
```

```{r}
labels <- c("0" = "Age 18-24", "1" = "Age 25-44", "2" = "Age 45-64", "3" = "Age 65+")

model_coef_plot <- ggplot(data = data3[which(data3$ID2 <200),], 
       mapping = aes(x = DaysPhase3.x, y = NAD, colour = ID)) +
  geom_point() +
  geom_abline(aes(intercept = Intercept, 
                  slope = DaysPhase3.y,
                  colour = ID),size = 0.5) + 
                  scale_x_continuous(limits = c(0, 100)) + 
                  theme(legend.position = "none") +
                  facet_wrap(~Age_new, 
                  labeller = labeller(Age_new = labels)) +
  xlab("Days since decline in peak stringency") +
  ggtitle("Predicted NAD trajectories for subsample of participants")  +
      theme_minimal(base_size=12) + 
      scale_color_discrete() + 
      theme(plot.title = element_text(hjust = 0.5)) +
      theme(legend.position = "none") 

model_coef_plot
``` 

# Random slope variation plot
```{r, message=F}
plot_NADp3_slope <- ggplot(data2, aes(x= DaysPhase3.y, fill = ..x..)) +
  geom_histogram() +
 scale_fill_viridis(option = "C") +
  theme_minimal()+
  theme(legend.position="none") + 
  labs(title="Variability in NAD trajectories after peak stringency",
       x="Regression coefficient (NAD ~ days)", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5)) +
   facet_wrap(~ Age_new, labeller = labeller(Age_new = Age_labels)) 

```

```{r}
plot_NADp3_slope 
```


```{r}
stargazer(coef_NADp1, coef_NADp2, coef_NADp3,
type="html", df = TRUE, out="star_coefallphase_NAD.doc",  single.row=TRUE, digits = 2, align = TRUE)

stargazer(model_NADp1, model_NADp2, model_NADp2q, model_NADp3,
type="html", df = TRUE, out="starallphasesNAD.doc",  single.row=TRUE, digits = 2, align = TRUE,
intercept.top = TRUE, intercept.bottom = FALSE)
```